### 2016-08-03 Engine.tex
1.修改构建AMT部分(完成);2.修改Verification部分(未完成)

\documentclass{article}

\usepackage[numbers]{natbib}
\citestyle{IEEEtran}

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{color}
\newcommand{\SWITCH}[1]{\STATE \textbf{switch} (#1)}
\newcommand{\ENDPWITCH}{\STATE \textbf{end switch}}
\newcommand{\CASE}[1]{\STATE \textbf{case} #1\textbf{:} \begin{ALC@g}}
\newcommand{\ENDCASE}{\end{ALC@g}}
\newcommand{\CASELINE}[1]{\STATE \textbf{case} #1\textbf{:} }
\newcommand{\DEFAULT}{\STATE \textbf{default:} \begin{ALC@g}}
\newcommand{\ENDDEFAULT}{\end{ALC@g}}
\newcommand{\DEFAULTLINE}[1]{\STATE \textbf{default:} }
\newtheorem{mydef}{Definition}
\newtheorem{mylm}{Proposition}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

% \title{An Efficient Adaptive Architecture for Muliti-pattern Matching}
% \author{Zhan Peng  Yuping Wang}
 %\maketitle

\begin{document}

\bibliographystyle{alpha}

\begin{center}
{\Large An Fast Engine for Large-scale String Pattern Matching}
\end{center}

\begin{abstract} 
  Multi-string matching is the core technique that is widely used in
  many applications. In general, it searches a text string for all
  occurrences of some string patterns. However, as the number of
  string patterns increases, most of the existing algorithms suffer
  from two issues: the long matching time, and the high memory
  consumption. To address these issues, in this paper, a fast matching
  engine is proposed for large-scale string matching problems. Our
  engine includes a filter module and a verification module. The filter
  module is based on several bitmaps, which is response for quickly
  filtering out the invalid positions in the text, while for each
  potential matched position, the verification module confirms true
  pattern occurrence. In particular, we design a compact data
  structure called Adaptive Matching Tree (AMT) as the verification
  module, in which each tree node saves some pattern fragments of the
  whole pattern set. The key point is that, the inner structure of
  each tree node is chosen adaptively according to the features of the
  corresponding pattern fragments, and this makes the whole AMT both
  time and space efficient for verifying. The experiments indicate
  that, our matching engine performs better than the prior algorithms,
  especially for large pattern sets.
\end{abstract}

{\textbf{Key words}: String Matching; Pattern Matching; Dictionary Matching}

due to the effectiveness of the filter and the compactness of the AMT
whether there are patterns starting at that position

\section{Introduction}
\label{sec:introduction}

String matching (SM) has been historically one of the key areas of
computer science. According to the number of strings to be matched
simultaneously, string matching technologies can be classified into
single string matching (SSM) and multi-string matching (MSM), and this
paper mainly focuses on the latter.

The MSM is a primitive but critical operation used in many
applications such as information retrieval, intrusion detection
system, information extraction, text editing, etc. In general, it
seeks all positions in a text string that match any of the string
patterns in a given pattern set. Efficient algorithms for MSM scan the
text only once, searching for all patterns
concurrently. Traditionally, these algorithms include two major
phases, i.e. the \textsf{preprocessing phase} and the \textsf{matching
  phase}. In the \textsf{preprocessing phase}, a suitable data
structure is constructed to store all the string patterns, and then
the \textsf{matching phase} scans and compares the given text with the
data structure for finding all occurrences every pattern in the
text. It is obvious that the time and space efficiency of the data
structure built in the preprocessing phase can have a significant
impact on the performance of the algorithm in the matching phase.

% Preferably, an algorithm scans the text once so that its performance
% should mainly depend on the size of the text rather than the features
% of pattern sets. However, the performance of lots of existing
% algorithms for MSM is affected seriously by the pattern sets. For
% instance, many algorithms, such as the classical \textsf{Wu-Manber}
% (\textsf{WM}) algorithm or the more recent \textsf{Pre-filter+AC}
% scheme, can not efficiently deal with the pattern sets containing very
% short patterns. When encountering such pattern sets, the performance
% of these algorithm degrades dramatically. This is due to the internal
% design of the data structure which is used for
% matching. {\color{red}{Therefore, it's quite valuable to design a data
% structure that can efficiently support pattern sets with various
% features. Using this kind of data structure can improve the robustness
% of MSM.}}

In the big data context nowadays the number of patterns to be matched
becomes huge in some applications, for instance, the database of a
modern anti-virus/intrusion-detection system can easily contain
millions, or even tens of millions number of virus
signatures/rules. However, the existing algorithms are not suitable
for such applications with very large pattern sets. Because on the one
hand, the throughout of these methods can not keep up with the demand
of the applications as the number of patterns increases, which is due
to the poor scalability of the data structures used by these methods,
and on the other hand, the data structure of several algorithms (such
as the \textsf{AC} algorithm) is not space efficient, which means they
can not process large pattern sets with limited memory. Therefore it
is very valuable to design space-efficient data structures with good
scalability to support applications requiring large-scale string
matching.

In this paper, we propose a multi-string matching engine for large
string pattern sets. Similarly to the traditional approaches, our
strategy consists of the preprocessing phase and the matching
phase. In the preprocessing phase, the matching engine is constructed
based on the pattern set. Then in the matching phase, the engine takes
the text string as input, and searches the occurrences of each
pattern in the text.

The proposed engine consists of a filter module and a verification
module. The function of the filter module is to find the potential matched
positions in the text. Once such a position is found, the verification
module confirms whether there are patterns starting at that
position. The filter we adopted is proposed by \cite{Lee2013}, which
is based on several bitmaps and a group of simple bitwised \emph{and}
and \emph{shift} operations. In the matching phase, the engine queries
the bitmaps to check the validity of the current position: if the
current position is a potential matched position, the verification
unit is invoked; otherwise, the engine skips over this position (as
well as the next few positions if possible). In particular, the
authors proved that the proposed filter is optimal in the sense that
it is able to utilizing all previous query results, which means the
filter can skip as many invalid positions as possible. For the
verification module, we design a compact tree-like data structure called
Adaptive Matching Tree (\textsf{AMT}) based on the pattern
set. Specifically, the whole pattern set is gradually partitioned into
several small parts first, and then the pattern fragments of each
small part is stored in a separate node of the AMT for subsequent
matching. The key point is that, the inner structure of each tree node
is selected adaptively according to the features of the pattern
fragments, and this adaptivity guarantees a high matching speed as
well as a low memory consumption for each tree node, as a result, the
whole AMT would be both time and space efficient for verifying in the
matching phase.

The rest of this paper is organized as follows: Section
\ref{sec:related works} reviews some related works in MSM. Section
\ref{sec:notations} lists the notations and terminology used in this
paper. Section \ref{sec:ADSM} describes our matching engine in
details. Section \ref{sec:experiments} presents the performance
evaluations. Section \ref{sec:conclusion} concludes the paper and
proposes some open problems.

\section{Related Works}
\label{sec:related works}

Because of the importance of PM, several efficient algorithms have
been proposed in the past decades. Well-known algorithms for PM
include Knuth-Morris-Pratt (\textsf{KMP}) \cite{Knuth1977},
Boyer-Moore (\textsf{BM}) \cite{Boyer1977}, Wu-Manber (\textsf{WM})
\cite{Wu1994}, and Aho-Corasick (\textsf{AC}) \cite{Aho1975}. The
\textsf{KMP} and \textsf{BM} algorithms are appropriate for SPM, but
not suitable for MPM. The \textsf{AC} algorithm is a generalization of
the \textsf{KMP} algorithm, by preprocessing the patterns and building
a deterministic finite automaton (DFA) that can match multiple
patterns simultaneously. It is the first algorithm for MPM that has a
linear time complexity. However, the \textsf{AC} algorithm is
alphabet-sensitive and requires a huge amount of memory to build the
DFA, which limits its application in large-scale pattern matching.

To reduce the memory requirement of \textsf{AC}, Tuck[2004] proposed a
algorithm called \textsf{Bitmapped AC}. This algorithm uses the bitmap
data structure to replace the conventional child pointers in each
state. In addition, it uses a path compression technique which can
merge successive single-child states into one state. It is reported
that, the compression optimization of \textsf{Bitmapped AC} results in
a 50 times reduction in memory consumption over the default
\textsf{AC} algorithm. However, since traversal from node to node
requires checking a bit in a bitmap and then performing a sum up to
256 prior bits in the bitmap, the average performance of this
algorithm is not high.  Another algorithm to reduce the space
requirement is the \textsf{Compressed AC} algorithm proposed by
Bremeler-Barr[2011]. In addition to use a similar path compression
method, this algorithm also develops a technique that can eliminate
the leaf states. The experiment shows that \textsf{Compressed AC} can
reduce at most $60\%$ memory requirement compared with the
traditionally \textsf{AC} algorithm. But the similar problem is, it
only works well for a few pattern sets.  Lee[2013] proposed an
algorithm called \textsf{Pre-filter+AC}. As the name shows, this
algorithm consists of a pre-filter and a verification engine. The
function of the pre-filter is to query data structures built from
patterns to find the starting positions of potential pattern
occurrences. Once a suspicious starting position is found, the
verification engine confirms true pattern occurrence. The pre-filter
uses a bit vector, called master bitmap, with simple bitwise-AND and
shift operations to accumulate query results. While the verification
engine, which is a modification of the AC automaton, checks all
candidate patterns simultaneously rather than sequentially. However,
as the author stated, the pre-filter is suitable for patterns of
moderate or large lengths. For short patterns, its throughput
degrades.

The \textsf{WM} algorithm is another efficient algorithm for MPM which
is known to be faster than \textsf{AC} in a typical matching. The
\textsf{WM} algorithm is an adaptation of the \textsf{BM} algorithm to
multiple patterns. It uses a similar ``shift idea'' of the \textsf{BM}
algorithm, but the shift of \textsf{WM} is not based on a single
character as the \textsf{BM} does, instead, it is based on a
$B$-$gram$ that is a character block consists of $B$ characters ($B$
is usually set to 2 or 3 in practice). In a typical search, its time
complexity is $O(B \cdot n/lsp)$, where $lsp$ is the length of the
shortest pattern in the pattern set. Therefore, the performance of WM
is seriously affected by $lsp$.

To improve the \textsf{WM} algorithm, Zhou \cite{Zhou2007} proposed an
algorithm called \textsf{MDH}. Instead of using the first $m$
characters as the signature of each pattern, \textsf{MDH} adopts a
heuristic strategy to select the optimum $m$ consecutive characters as
the signature of each pattern. Similarly, Zhan \cite{Zhan2014}
proposed a different way to search for the optimal signatures of the
patterns, additionally, this algorithm designs an index structure to
reduce the time for searching the candidate patterns in the Hash
Table. These algorithms can improve the performance of \textsf{WM} for
common patterns but they do not solve the inefficiency caused by short
patterns. To address this problem, Zhang \cite{Zhang2009} proposed the
High Concurrence WM algorithm (\textsf{HCWM}), which separates the
patterns whose length is less than 4 from the pattern set. For these
short patterns, the algorithm establishes independent data structures
and uses different matching routines. This method can reduce the
effect of short patterns, since short patterns are matched
independently and concurrently. Another algorithm for this problem is
the \textsf{$L^{+1}$-MWM} proposed by Choi \cite{Choi2011}, which
minimizes the performance degradation caused by the short patterns by
appending characters to these patterns. It is reported that, the
\textsf{$L^{+1}$-MWM} improves the performance of WM by as mush as
$20\%$ in average, moreover, when $lsp < 5$ the \textsf{$L^{+1}$-MWM}
gains an $38.87\%$ enhancement.

For large scale pattern matching, which becomes more and more
important in big data context, Le \cite{Le2013} presented a
Memory-efficient Architecture for large-scale String Matching
(\textsf{MASM}) based on a pipelined binary search tree. It uses a
technique called ``leaf-attaching'' to compress the given pattern
set. The compressed pattern set are then transformed to a pipelined
binary tree tree which will be used in the matching phase. It is
reported that, the \textsf{MASM} achieves a memory efficiency (defined
as the ratio of the amount of the required storage in bytes and the
size of the pattern set in number of characters) of 0.56 for the
Rogets dictionary and 1.32 for the Snort rule set. Moraru
\cite{Moraru2012} also presented a memory-efficient and
cache-optimized algorithm for large pattern sets. This algorithm
builds upon the Rabin-Karp \cite{Karp1987} SPM algorithm and
incorporates a new \textsf{feed-forward} bloom filter which takes into
account the memory hierarchy of modern computers. This algorithm is
also well suited for implementation on GPUs which enables the matching
to be done in parallel.

There are also studies that exploited the capacity of hardware to
accelerate the proposed MPM engines. Agarwal \cite{Agarwal2013}
proposed a hardware architecture which enables high throughout for
Information Extraction applications. Instead of using the common DFA
based approach, this architecture employs a novel hashing based
scheme. The DFA based approaches (such as \textsf{AC}) typically
process one character every cycle, while the proposed hash based
scheme can process a string token of several characters every cycle,
thus achieves higher throughout than the DFA based approaches. Zhang
\cite{Zhang2015} proposed an GPU-based parallel algorithm
\textsf{G-PEBF} which uses the Extended Bloom Filter (EBF). It divides
the pattern set into $N$ subsets where the lengths of the patterns in
each subsets are the same. Then it constructs an EBF for each subset
and uses $N$ threads to simultaneously process the subsets in parallel
on the GPU. The performance of \textsf{G-PEFB} highly relies on the
number of threads used during matching, and it is also not applicable
for pattern sets containing very short patterns.

Nowadays, some variants of the classical MPM problem have been
proposed. Tomohiro \cite{I2015} introduced a variant of MPM, where the
pattern set is given in a compressed form that can be represented by a
straight line program (SLP). For a given SLP-compressed pattern set of
size $n$ and height $h$, which represents $m$ patterns of total length
$N$, they present an $O(n^2log^N)$-size variant of AC automaton that
recognizes all occurrences of the patterns in $O(h + m)$ running time
per character. Khancome \cite{Khancome2013} proposed an algorithm for
the dynamic MPM problem. This algorithm uses the \textsf{inverted
  lists} data structure to allow the pattern set to be updated
dynamically in a optimal time. Amir \cite{Amir2015} introduced an
algorithm for the gapped MPM problem, where each pattern in the
pattern set is a sequence of sub-patterns separated by bounded
sequences of do not cares. Neuburger \cite{Neuburger2012} presented
the first efficient algorithm that operates in small space for the
2-dimensional MPM problem.

\section{Notations}
\label{sec:notations}

Let $\Sigma$ be an \textsf{alphabet} consisting of a finite number of
character symbols. (In this paper we will only focus on the case that
$\Sigma$ is the ASCII character set, i.e. $|\Sigma| = 256$ and each
character takes one byte memory.) Given the alphabet $\Sigma$, a
\textsf{string} as well as its \textsf{substrings} over
$\Sigma$ can be defined as follows:\\
\\
\textbf{Definition 1.} A \textsf{string} over $\Sigma$ is a sequence
consisting of a finite number of characters from $\Sigma$. A
length-$n$ string is represented by $S = c_1c_2..c_n$, where the
$i$-th character of $S$ is: $S[i] = c_i \in \Sigma$
$(1 \leq i \leq n)$. The length of $S$ is denoted by $|S|$. A
\textsf{substring} of $S$ is a sequence consisting of any consecutive
characters of $S$. The substring of $S$, which starts at
position $i$ and has length $len$, is denoted by $S[i,\,len]$.\\
\\
Given a string $S$, its \textsf{prefix} and \textsf{suffix},
which are both special substrings of $S$, are defined as follows:\\
\\
\textbf{Definition 2.} The length-$m$ \textsf{prefix} of a string $S$,
which is denoted by $S^{+m}$, is the substring that consists of the
first $m$ characters of $S$, i.e. $S^{+m}=S[1,\,m]$.  While the
\textsf{suffix} of $S$ that starts at position $m+1$, is the substring
left after removing the length-$m$ prefix of $S$. It is
denoted by $S^{-m}$, i.e. $S^{-m} = S[m+1,\,|S|-m]$.\\
\\
Actually, a string $S$ can be regarded as a prefix/suffix of itself,
i.e. $S=S^{+|S|}=S^{-0}$. Finally, the MSM problem can be
formally defined as follows: \\
\\
\textbf{Definition 3.} Given a text string $T$ and a pattern set
$P=\{p_1,\,p_2,\,\dots,\,p_k\}$, where $T$ and $p_i$
$(1 \leq i \leq k)$ are all strings over $\Sigma$.  The multi-string
pattern matching is to find all occurrences of every pattern of $P$ in
$T$, more formally, to build the result set
$R = \{(i,\, p_j)\;|\; p_j \in P\; and\,\; T[i,\,|p_j|]=p_j\}$.

\section{The Filter Module}
\label{sec:filter}

As mentioned before, our engine consists of the filter module and the
verification module. In this section, we introduce the filter module,
while in the next section the verification module will be illustrated.

% the whole pattern set is transformed to a compact tree-like structure
% called Adaptive Matching Tree (AMT), where each tree node is built
% adaptively to save the information of a small part of the pattern
% set. While in the matching phase, the built AMT is compared against
% the text string to search patterns in that string. The framework of
% constructing the AMT from the pattern set is introduced in Section
% \ref{subsec:amt}, and using the AMT to search patterns in the text
% string is described in Section \ref{subsec:matching}, finally
% adaptively creating the tree nodes is presented in Section
% \ref{subsec:nodes}.

The filter we adopted in our engine is proposed by
\cite{Lee2013}. Given the pattern set, as in the WM algorithm, only
the length-$lsp$ prefix of each pattern are considering in
constructing the filter, where $lsp$ is the \emph{length of the
  shortest pattern} in the pattern set. Similar to WM, the filtering
is based on character blocks (a character block is a short string
consisting of only a few characters) rather than single
characters. Given a block size $k$, the filter includes $lsp-k+1$
membership query bitmaps denoted as $B_1$, $B_2$, \dots, and
$B_{lsp-k+1}$, where each bitmap is a vector of $N$ bits. Let
$B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be the
$i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1 iff
there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
where $hash$ is a hash function that maps a $k$-symbol block to an
integer in the range of $[0, N-1]$.

Fig shows an example, assume that alphabet
$\Sigma = \{0, 1, 2, \dots, 9\}$ and pattern set
$P = \{p_1,\; p_2,\; p_3\}$, where $p_1 = 04648753$, $p_2 = 30692$,
and $p_3 = 614621$. Obviously, there is $lsp = |p_2|= 5$. Assume that
$k = 2$, $N = 100$, and the hash function is the identity mapping. For
such a setting, there are $lsp - k + 1 = 4$ query bitmaps, i.e. $B_1$,
$B_2$, $B_3$, $B_4$, and in particular, we have $B_1[i] = 1$ iff $i$ =
4, 30, or 61; $B_2[i] = 1$ iff $i$ = 6, 14, or 46; $B_3[i] = 1$ iff
$i$ = 46, 64, or 69; and $B_4[i] = 1$ iff $i$ = 48, 62, or 92.

% In addition, another bitmap of $lsp-k+1$ bits, which is called
% \emph{master bitmap} and denoted by
% $MB = mb_1mb_2 \dots mb_{lsp-k+1}$, is adopted to accumulate the
% previous query results and act as the current state of the filter.

Once the query bitmaps have been constructed, they can be used to
filter the positions of the input text string. During filtering, a
sliding window $W$ of length $lsp$ is adopted to select a segment of
the text string $T$. Initially, $W$ is aligned with the beginning of
$T$, so that the substring of $T$ contained in $W$ is $T[1,lsp]$. In
general, assume that $W$ is moved to the $i$-th position of $T$, and
the substring of $T$ contained in $W$ is $T[i,lsp]$. Then the last
$k$-symbol block of $T[i,lsp]$, which is $T[i+lsp-k, k]$, is used to
query all the bitmaps. Let single bit $qb_j$ be the report of $B_j$
($1 \leq j \leq lsp - k + 1$), and $qb_j=1$ iff
$B_j[hash(T[i+lsp-k,k])] = 1$. Let bitmap
$QB = qb_1qb_2 \dots qb_{lsp-k+1}$ to denote the current query result
and another \emph{master bitmap} $MB = mb_1mb_2 \dots mb_{lsp-k+1}$ to
accumulate the previous query results and act as the current state of
the filter. Initially, all the bits of $MB$ are set to 1. After
fetching a query result $QB$, the master bitmap is updated by
$MB = MB \; \& \; QB$, where \& is the bitwised-AND operation. For the
updated $MB$, if $mb_{lsp-k+1} = 1$, position $i$ is considered as a
potential matched position and the verification module is
invoked. Otherwise, the sliding window $W$ is advanced by $lsp-k+1$
positions if all the bits of $MB$ are 0's, or $lsp-k+1-r$ positions if
$mb_r=1$ and $mb_i=0$, for $r < i \leq lsp-k$. The positions skipped
by $W$ are filtered out. If $W$ is determined to be advanced by $h$
positions, $MB$ is right-shifted by $h$ bits and filled with 1's for
the holes left by the shift. Particularly, it is proved in
\cite{Lee2013} that the proposed filter using master bitmap and simple
bitwised AND and SHIFT operations is optimal in the sense that it is
able to utilize all previous query results, which means the filter can
filter out as many positions as possible in the text.

As an example, consider the query bitmaps constructed above and assume
that $T=23764614621$. Initially, the matching window $W$ contains
23764 and $MB = 1111$. The last 2-symbol block of $W$, i.e. 64, is
used for the first query, and the query result is $QB=0010$. Since
$MB\; \&\; QB = 0010$, $W$ is advanced by 1 position (which means the
first position of $T$ is filtered out), and then $MB$ is updated as
$1001$ by right shift. For the second position, the substring
contained in $W$ is 37646.  This time, block 46 is used to query the
bitmaps and the query result is $QB=0110$. Since $MB\; \& \; QB=0000$,
$W$ moves forward by 4 positions to position 6 (which means positions
$2 \sim 5$ are filled out), and $MB$ is updated as 1111. For position
6, $W$ contains 61462 and block 62 is used for querying and fetches
$QB = 0001$. Since $MB\; \& \; QB = 0001$, position 6 is a potential
matched position, and then the verification module is invoked. After
checking, the pattern $p_3=614621$ is detected at position 6. Then,
$W$ is advanced by 4 positions to position 10. However, since the
length of the remaining input text in $W$, i.e. 21, is smaller than
$lsp$, which means there can not be any pattern starting at that
position, the whole scanning procedure is terminated.

% The core idea of the filter is to use the length-$lsp$ prefix of each
% pattern as the \textsf{signatures}, and then use the signatures to
% check the validity of each position. In particular, if the current
% position of the text (roughly) matches a signature, which means the
% position may match the corresponding pattern, the current position is
% a potential matched position; otherwise, if the current position does
% not match any signature, this position can not match any pattern
% either and can be safely filtered out.

\section{The verification module}
\label{sec:verification}

The verification module is the core of the whole matching engine,
since it determines the worst case performance of the engine. The
verification module in our engine is based on a new data structure
called \emph{Adaptive Matching Tree} (AMT) which is a modification of
the classical \emph{trie} structure. Like the \emph{trie}, but in a
more flexible and space efficient way, the AMT enables a fast
membership query which decides whether a given target string exists in
the pattern set. In the next subsections, we will introduce the
construction of the AMT, constructed AMT, and a some further
optimization techniques.

\subsection{AMT Construction}
\label{subsec:amt}

The AMT is constructed from the pattern set, and in general, this
construction includes five major steps:

\begin{enumerate}
\item Create a suffix set $SF$, and put each pattern of the pattern
  set into $SF$, where each pattern is regarded as a suffix of itself.
\item Compute the \emph{length of the shortest suffix} ($lss$) in
  $SF$. For each suffix in $SF$, remove its length-$lss$ prefix, and
  all the removed prefixes form a prefix set $PF$. Discard the
  repetitions in $PF$, and calculate $|PF|$ which refers to the
  \emph{number of distinct prefixes} ($ndp$).
\item Create a tree \emph{node} to hold the prefixes in $PF$. The
  \emph{node} is actually an index, in which each prefix serves as a
  key. The inner structure of the \emph{node} is constructed
  adaptively according to $ndp$ and $lss$ that have been computed in
  step 2.
\item Divide $SF$ by putting together all its suffixes who have the
  same prefix removed, to form a sub-suffix-set. Associate each
  sub-suffix-set with the corresponding prefix in the tree \emph{node}.
\item For each newly created sub-suffix-set in step 3, repeat the same
  procedure from step 2.
\end{enumerate}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{./eps/AMT}
  \caption{Constructing the AMT from a pattern set. Each arrow
    in the AMT indicates a child pointer.}
  \label{fig:AMT}
\end{figure}

As an example, Figure \ref{fig:AMT} shows of the construction of AMT
from a pattern set $P = \{p_1,\, p_2,\, \dots,\, p_{13}\}$. Note that,
since each pattern is a suffix of itself, the whole pattern set $P$
can be also regarded as a suffix set $SF$. First, since $p_6$ is the
shortest pattern(suffix) in $P$, we have $lss = |p_6| = 2$. Then the
length-2 prefix of each pattern(suffix) is removed, and the removed
prefixes form a prefix set:
$PF = \{p_1^{+2} = aa,\; p_2^{+2} = aa,\; \dots,\; p_{13}^{+2} =
cc\}$. After discarding the repetitions in $PF$, only 3 distinct
prefixes are left: $PF = \{aa,\, bb,\, cc\}$, and we have
$ndp = |PF| = 3$.

Then the first tree node, which is actually the root of AMT, is
created to hold the prefixes in $PF$. Each prefix serves as a
\emph{key} in the root and has a pointer (initialized to $NULL$) which
will be used to associate with the child node in the future. As will
be seen latter, the structure of root is selected adaptively according
to two parameters: $lss=2$ and $ndp=3$.

After creation of the root, the suffixes left in $P$ are grouped based
on their lost 2-symbol prefixes: those suffixes having the same
prefixes removed are grouped together to form a sub-suffix-set. In
order to record the correspondence between the sub-suffix-set and the
lost prefix, the tuple (\emph{node.key,\; sub-suffix-set}) is used:
the suffixes in the \emph{sub-suffix-set} have the same prefix
\emph{key} removed, where the \emph{key} is held as a key in the newly
created \emph{node}. Using this notation, there are three tuples
created after grouping the suffixes left in $P$:
$tp_1 = (root.aa,\; SF_1=\{p_1^{-2},\, p_2^{-2},\, p_3^{-2},\,
p_4^{-2},\, p_5^{-2},\, p_7^{-2}\})$,\,
$tp_2 = (root.bb,\; SF_2=\{p_8^{-2},\, p_9^{-2},\, p_{10}^{-2}\})$ and
$tp_3 = (root.cc,\; SF_3=\{p_{11}^{-2},\, p_{12}^{-2},\,
p_{13}^{-2}\})$. This indicates that $P$ is divided into three
sub-suffix-sets: $SF_1$, $SF_2$, $SF_3$, and each sub-suffix-set
corresponds to a prefix held as a key in the root (it also means that
the root may have three child nodes). Note that, the shortest
suffix(pattern) $p_6$ has disappeared in the sub-suffix-sets, since
after removing the length-2 prefix of $p_6$, there is nothing left.

The same procedure is repeated upon each of the three created
sub-suffix-sets. As a further example, $SF_1$ of $tp_1$ is
processed. First, since $lss = |p_7^{-2}| = 6$, the length-$6$ prefix
of each suffix in $SF_1$ is removed to form a prefix set:
$PF_1 = \{(p_1^{-2})^{+6},\, (p_2^{-2})^{+6},\, (p_3^{-2})^{+6},\,
(p_4^{-2})^{+6},\, (p_5^{-2})^{+6},\, (p_7^{-2})^{+6}\}$. After
discarding the duplicates in $PF_1$, only three distinct prefixes are
left: $PF_1 = \{a^6,\, e^6,\, b^6\}$ (we use the notation $c^n$ to
denote a length-$n$ string consisting of the same character $c$). Then
a new tree node $node_1$ is built adaptively upon $PF_1$ to hold its
prefixes as keys.  According to the first component of $tp_1$
(i.e. $root.aa$), $node_1$ is associated with the key $aa$ in the root
by a child pointer, which makes it to be the first child of root. Once
again, the suffixes left in $SF_1$ are grouped based on their lost
length-6 prefixes, which formed three new tuples:
$tp_4 = (node_1.a^6,\; SF_4=\{p_1^{-8}\})$,
$tp_5 = (node_1.e^6,\; SF_5=\{p_2^{-8},\, p_3^{-8},\, p_4^{-8}\})$ and
$tp_6 = (node_1.b^6,\; SF_6=\{p_5^{-8}\})$.

Note that, in order to mark the end of a pattern, once the last part
of the pattern has been removed and then stored in a node, that last
part is marked with an asterisk(*) in the corresponding node. As a
result of this, any path from the root to a key that marked with an
asterisk represents a complete pattern. From this it can be seen that,
the patterns are stored implicitly in the AMT and can be reconstructed
from the paths ended with an asterisk.

During the construction of AMT, we use a \emph{breadth-first} strategy
to process the sub-suffix-sets and create tree nodes (which means the
next sub-suffix-set to be processed is $SF_2$ rather than $SF_4$). For
the purpose of tracing the order in which the sub-suffix-sets are
processed, a \emph{first-in-first-out} queue is employed to maintain
the created tuples. The tuple at the beginning of the queue contains
the sub-suffix-set that will be processed next, while the newly
created tuples are inserted to the end of the queue in order. In our
example, the root node is built initially, then $tp_1$, $tp_2$ and
$tp_3$ are inserted to the queue. Next $SF_1$ of $tp_1$ is processed
and the newly created tuples $tp_4$, $tp_5$ and $tp_6$ are inserted to
the queue in order. Subsequently, $SF_2$, $SF_3$, $SF_4$, $SF_5$,
$SF_6$, $\dots$ are processed in sequence. Once there is no tuple left
in the queue, the whole AMT has been constructed.

\begin{algorithm}
  \caption{Constructing the AMT}\scriptsize
  \label{alg:amt}
  \begin{algorithmic}[1]
    \REQUIRE The pattern set $P$
    \ENSURE The corresponding AMT
    \STATE
    \STATE $Q \leftarrow$ Create an empty queue
    \STATE $push\_queue((NULL,\,P),\; Q)$
    \STATE
    \WHILE{$Q$ is not empty}
    \STATE $(parent\_node.key,\; SF) \leftarrow pop\_queue(Q)$
    \STATE $lss \leftarrow$ The length of the shortest pattern in $SF$
    \FOR{each $suf \in SF$}
    \IF{$|suf|=lss$}
    \STATE Mark $suf^{+lss}$ to be the pattern end
    \ENDIF
    \STATE Remove $suf^{+lss}$ of $suf$, and put $suf^{+lss}$ into $PF$
    \ENDFOR
    \STATE Discard the repetitions in $PF$, and let $ndp \leftarrow |PF|$
    \STATE According to $lss$ and $ndp$, adaptively create a
    $new\_node$ to hold the prefixes in
    $PF$
    \IF{$(parent\_node.key = NULL)$}
    \STATE $root \leftarrow new\_node$
    \ELSE
    \STATE Associate $new\_node$
    with $parent\_node.key$ by a child pointer
    \ENDIF
    \STATE $TP \leftarrow \{(new\_node.pf,\, SSF) \mid SSF \subseteq SF\; and
    \ \forall \ p,\,q \in SSF: p,\,q$ have the same length-$lss$ prefix
    $pf$ removed\}\
    \FOR{each $tp \in TP$}
    \STATE $push\_queue(Q,\,tp)$
    \ENDFOR
    \ENDWHILE
    \STATE
    \RETURN $root$.
  \end{algorithmic}
\end{algorithm}

The framework of constructing the AMT from a pattern set is
illustrated in Algorithm \ref{alg:amt}. Firstly, an empty queue $Q$ is
created in line 2 for maintaining the tuples. Then the tuple
$(NULL, P)$ is inserted to $Q$ in line 3 by function $push\_queue$
which always inserts an element to the end of the queue. Since $P$ is
the initial pattern set here, the first component of the tuple is
$NULL$, which means there is no prefix removed from $P$ yet. By this
way, the creation of the root can be combined with the creation of
other tree nodes in the following \textbf{while} loop.

If $Q$ is not empty, the \textbf{while} loop body from line 5 to line
25 constructs a tree node based on the first tuple in $Q$. The tuple
at the beginning of $Q$ is fetched by the $pop\_queue(Q)$ function in
line 6: the suffix set to be processed is assigned to $SF$, and the
corresponding prefix of $SF$ in the parent node is denoted by
$parent\_node.key$. Then the $lss$ of $SF$ is computed in line 7. In
the inner \textbf{for} loop from line 8 to line 13, the length-$lss$
prefix of each suffix in $SF$ is removed, and the prefixes are
collected to form the prefix set $PF$. If a prefix is the last part of
some pattern, it is marked as a pattern end. Line 14 discards the
repetitions in $PF$, after that, a new tree node is created adaptively
to hold the prefixes $PF$ in line 15. The \textbf{if} statement in
line 16 decides whether the newly created node is the root node or
not: if the prefix component of the current tuple is $NULL$, the new
node is the root node as stated before; otherwise, the new node is a
child node which will be then associated with the corresponding prefix
in its parent node. Next in line 21, the suffixes left in $SF$ are
grouped based on their lost prefixes, and each group and the
corresponding prefix forms a tuple. Finally, the created tuples are
inserted orderly to the end of $Q$ by the $push\_queue$ function. Once
there is no tuple left in $Q$, the whole AMT has been completely
constructed, and the root of AMT is returned.

\subsection{Verification}
\label{subsec:matching}

As stated in the filtering phase, once a suspicious position in the
text has been detected by the filter module, the verification module
checks that position for real pattern occurrences. In particular, for
such a suspicious position $i$, the engine searches a sequence of
substrings of the text, where the first substring starts at $i$, in
the corresponding nodes in AMT from the root. If the text successfully
matched a key that is marked as a pattern end in some node, a pattern
is declared to be found at position $i$. However, if there is a
mismatch or the searching goes beyond the leaves of AMT, the engine
forwards to the next position of the text and invokes the filter.

The pseudocode of verifying is shown in Algorithm
\ref{alg:matching}. Suppose $i$ is a suspicious position in the
text. The $m\_len$ is the total length of the successfully matched
sub-strings of the text. The $node$ points to the current matching
node in the AMT. In addition, since all the keys in a node have the
same length, the notation $key\_len(node)$ is used to denote the
length of the keys in $node$.

\begin{algorithm}
  \caption{Verification}\scriptsize
  \label{alg:matching}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A suspicious position $i$ in the text $T$\\
    The AMT built from the pattern set $P$\\
    \ENSURE ~~\\
    The patterns start at $i$ (if any)
    \STATE
    \STATE $m\_len \leftarrow 0$
    \STATE $node \leftarrow root$ of AMT
    \STATE
    \WHILE{$node \neq NULL$ and $\exists key \in node: key =
      T[i+m\_len, \, key\_len(node)]$}
    \STATE $m\_len \leftarrow m\_len + key\_len(node)$
    \IF{$key$ is marked as a pattern end}
    \STATE The pattern $T[i,\,m\_len]$ is found at position $i$
    \ENDIF
    \STATE $node \leftarrow$ The child of $node.key$
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

For the suspicious position $i$, the \textbf{while} loop from line 5
to line 11 checks whether there are patterns starting at $i$. The
checking starts form the root of AMT: if the corresponding sub-string
$T[i+m\_len, \, key\_len(node)]$ matches some $key$ in the current
$node$, the totally matched length $m\_len$ is increased by the length
of the key. At the same time, if the matched $key$ is also marked as a
pattern end, the engine will report that a pattern, which is
$T[i,\,m\_len]$, is found at position $i$. Then the matching transfers
to the child of $node.key$ and makes that child node to be the current
node. Once there is a mismatch or the current node goes beyond the
leaves of AMT (i.e.  $node = NULL$), the verification terminates, and
the engine forwards to the next position $i+1$.

Note that, since the nodes in AMT have various types of inner
structures, the search of the target string in a node, must use the
search routine specified to the type of that node.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/match}
  \caption{The matching round that searches patterns starting at
    position $i$ of the text.}
  \label{fig:matching}
\end{figure}

Next, an example is given in figure \ref{fig:matching} to illuminate
the verification for position $i$ of a given text string $T$, using
the AMT built in section \ref{subsec:amt}. The matching round starts
from the root of AMT: according to $key\_len(root)=2$, the same length
sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
taken to check whether it's one of the keys in root. The result is
that: $aa \in root$, and also $aa$ is marked as a pattern
end. Therefore the pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is
found at position $i$. Then the matching transfers to $node_1$, which
is the child node of $root.aa$.

At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
$T[i+2,\,6]=e^6$, which appears following $T[i,\,2]$, is trying to
match with some key in $node_1$. The result is that: $e^6 \in node_1$
but it is not marked as a pattern end. Then the matching simply
transfers to $node_5$, which is the child of $node_1.e^6$.

At $node_5$, since the next sub-string $T[i+8,\,5]=u^5 \in node_5$ and
$u^5$ is marked as a pattern end, another pattern
$T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
$i$. Then the matching goes to the child of $node_5.u^5$, i.e.
$node_{10}$.

At $node_{10}$, since $T[i+13,\,4]=sscc \notin node_{10}$, the current
matching round for position $i$ terminates. The algorithm restarts a
new matching round for the next position $i+1$. Once all the positions
of the text have been checked, the whole algorithm terminates.

In our approach, each matching round actually corresponds to a
\textsf{matching path} in the AMT, whose tree nodes have been compared
with the text in the former matching process. In particular, the
matching path of the given example is:
$root \rightarrow node_1 \rightarrow node_5 \rightarrow node_{10}$,
witch is indicated by the dashed arrows in Figure \ref{fig:matching}.

\subsection{Adaptive creation of the tree nodes}
\label{subsec:nodes}

As stated in section \ref{subsec:amt}, each node of AMT has a specific
structure to hold the prefixes of a prefix set as the keys. The type
of the node structure is chosen adaptively according to the features
of the prefix set. Since all the keys in the prefix set have the same
length, the features of the prefix set can mainly be characterized by
two parameters: the \textsf{length} and \textsf{number} of the keys in
the prefix set. These two parameters are respectively symbolized by
$lss$ and $ndp$ in Section \ref{subsec:amt}.

In this work, three kinds of structures, i.e. \textsf{character map},
\textsf{string array} and \textsf{hash table} can be adopted for
prefix sets with different $lss$ and $ndp$ combinations. Next, the
detailed descriptions of them will be presented.

\subsubsection{Character map}

Given a prefix set, if the length of keys is equal to 1 ($lss=1$),
i.e. each key in the prefix set is just a single character, we adopt
the space-efficient \textsf{character map} structure, which was
proposed by Leis \cite{Leis2013}, as the tree node. There are four
sub-types of character maps with different capacities for different
number of keys ($ndp$), where $1 \leq ndp \leq 256$.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/Maps}
  \caption{The four sub-types of character maps. The triangles
    represent the corresponding child nodes.}
  \label{fig:character map}
\end{figure}

Figure \ref{fig:character map} illustrates the four sub-types of
character maps which are named according to their maximum
capacity. Instead of using an array of (\emph{key, child pointer})
pairs, the key part and the child pointer part are stored in the
separate arrays, which is able to keep the node information compact
while supporting efficient search.

\begin{itemize}
\item \textbf{Map 4} (for $1 \leq ndp \leq 4$): The smallest map type
  can store up to 4 keys. It uses an array of 4 entries for keys and
  another array of the same length for child pointers. The keys and
  child pointers are stored at corresponding positions in their
  arrays, and the keys are sorted according to their ACSII
  values. Once the target character is found in the key array, its
  child pointer can be located through the same position in the
  pointer array. Figure \ref{fig:character map} (a) shows a Map 4
  structure with three keys: $a$, $b$ and $c$, where the triangles
  with the keys inside represent the corresponding child nodes.

\item \textbf{Map 16} (for $5 \leq ndp \leq 16$): This map type is
  used for storing 5 to 16 keys. It has the similar structure as Map
  4, but both arrays have up to 16 entries. A target character can be
  retrieved efficiently by a binary search in the key array. Figure
  \ref{fig:character map} (b) shows a Map 16 structure with 14 keys:
  $a \sim n$.

\item \textbf{Map 48} (for $17 \leq ndp \leq 48$): As the number of
  keys increases, searching in the key array becomes
  expensive. Therefore, maps with more than 16 (but less than 49) keys
  do not store the keys explicitly. Instead, a 256-element
  \textsf{index array} is used, which can be directly indexed by the
  ASCII value of the target character. This array stores only the
  \textsf{array indexes} (small inters in the range of $[0,47]$) of
  another pointer array that contains up to 48 child pointers. In this
  way, the storage space can be saved comparing with storing pointers
  directly, because each array index only requires one byte. Figure
  \ref{fig:character map} (c) shows a Map 48 structure, where the
  ASCII values of $a$, $b$ and $c$ are 97, 98 and 99 respectively.

\item \textbf{Map 256} (for $49 \leq ndp \leq 256$): The largest map
  type is simply an array of 256 child pointers with each pointer
  initialized to $NULL$. It is used for storing 49 to 256 keys.  In
  this kind of character map, the child node can be found directly
  through the array index which is the ASCII value of the target
  character. Different from other sub-types of character maps, in Map
  256, there is only one array and not necessary to carry out the
  additional indirect access. Therefore, if most entries are not
  empty, this representation is also very space efficient. Figure
  \ref{fig:character map} (d) shows a Map 256 structure, where only
  the pointer array is adopted.
\end{itemize}

For the sake of clarity, the pseudocode of searching in a node, whose
type is character map, is given in Algorithm \ref{alg:character map}.

\begin{algorithm}
  \caption{Searching in a node whose type is character map}\scriptsize
  \label{alg:character map}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is character map\\
    The target character $t\_ch$.
    \ENSURE ~~\\
    The child node of $node.t\_ch$ (possibly $NULL$).
    \STATE
    \STATE $count \leftarrow$ Number of keys in the character map
    \STATE
    \SWITCH{the sub-type of the character map}
    \CASE{\textsf{Map 4}}
    \FOR{$i \leftarrow 0$ to $count-1$}
    \IF{$keys[i]=t\_ch$}
    \RETURN $child\_pointers[i]$
    \ENDIF
    \ENDFOR
    \RETURN $NULL$
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 16}}
    \STATE $low \leftarrow 0, high \leftarrow count-1$
    \WHILE{$low \le high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_ch=keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_ch<keys[mid]$}
    \STATE $high \leftarrow mid-1$
    \ELSE
    \STATE $low \leftarrow mid+1$
    \ENDIF
    \ENDWHILE
    \RETURN $NULL$
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 48}}
    \IF{$index[t\_ch] \neq NULL$}
    \RETURN $child\_pointers[index[t\_ch]]$
    \ELSE
    \RETURN $NULL$
    \ENDIF
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 256}}
    \RETURN $child\_pointers[t\_ch]$
    \ENDCASE
    \ENDPWITCH
  \end{algorithmic}
\end{algorithm}

\subsubsection{String array}
\label{sec:string array}

For the prefix set whose length of keys is greater than 1 ($lss > 1$)
and the number of keys is not greater than 100 ($ndp \leq 100$), the
\textsf{string array} structure is constructed as a tree node. Similar
to the character map, the keys are stored in lexicographical order in
a separate key array of $ndp \times lss$ bytes, in which each key
takes $lss$ bytes. The child pointers are stored at the corresponding
positions in another pointer array of $8 \times ndp$ bytes, where each
pointer takes 8 bytes in a typical x86\_64 architecture. Figure
\ref{fig:string array} illustrates a string array structure holding
there keys: $aaa$, $bbb$ and $ccc$. The key and pointer arrays occupy
9 and 24 bytes respectively.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.45\textwidth]{./eps/string_array}
  \caption{The string array structure with three keys: $aaa,\, bbb,\,
    ccc$.}
  \label{fig:string array}
\end{figure}

For efficiency, if the number of keys is less than 5, a naive linear
search routine is used to search the target string in the key array;
otherwise, a more efficient (but complicated) binary search algorithm
is adopted.  The pseudocode of the searching in a node whose type is
string array is depicted in Algorithm \ref{alg:string array}, where we
use the notation $A \prec B$ to denote that string $A$ is
\textsf{lexicographically smaller} than string $B$. For the string
array whose number of keys is less than 5, the target string is
compared sequentially with the keys in the key array. If the target
string matched some key, return the child pointer at the corresponding
position in the pointer array; otherwise, return $NULL$. On the other
hand, if the number of keys is greater than 4, the target string is
searched by a binary search routine from the middle element of the key
array.

\begin{algorithm}
  \caption{Searching in a node whose type is string array}\scriptsize
  \label{alg:string array}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is string array; \\
    The target string $t\_str$.\\
    \ENSURE ~~\\
    The child node of $node.t\_str$ (possibly $NULL$).\\
    \STATE
    \STATE $count \leftarrow$ The number of keys in $node$
    \STATE
    \IF{$count < 5$}
    \STATE $i \leftarrow 0$
    \WHILE{$i < count$ and $keys[i] \prec t\_str$}
    \STATE $i \leftarrow i+1$
    \ENDWHILE
    \IF{$i < count$ and $keys[i]=t\_str$}
    \RETURN $child\_pointers[i]$
    \ELSE
    \RETURN $NULL$
    \ENDIF
    \ELSE
    \STATE $low \leftarrow 0$, $high \leftarrow count-1$
    \WHILE{$low \leq high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_str = keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_str < keys[mid]$}
    \STATE $high \leftarrow mid - 1$
    \ELSE
    \STATE $low \leftarrow mid + 1$
    \ENDIF
    \ENDWHILE
    \RETURN $NULL$
    \ENDIF
  \end{algorithmic}
\end{algorithm}

\subsubsection{Hash table}
\label{sec:hash table}

For the prefix set whose number of keys is greater than 100 ($lss > 1$
and $ndp > 100$), searching in the string array structure becomes
inefficient even using a binary search. In this case, a more fast (but
heavy) data structure --- \textsf{hash table} is adopted to deal with
large number of keys. In this work, a hash table is an array of child
pointers with each pointer initialized to $NULL$, and we utilize a
\textsf{string hash function} which transforms a string to a positive
integer. It is worth noting that, the procedure of building a hash
table is directly based on the suffix set rather than the prefix set
which is the basis of building other structures.

% Indeed, when computing $ndp$, we
% merely count rather than really constructing the prefix set and then
% computing its $ndp$

In particular, given a suffix set $SF$, the size of the hash table
(denoted by $table\_size$) is determined by $ndp$ and a given
\textsf{load factor} $lf$ (ratio of $ndp$ to $table\_size$), i.e.
$table\_size = \lceil ndp\,/\,lf \rceil$. For example, with the $ndp$
of 1000 and a load factor of $70\%$, the $table\_size$ is
$\lceil 1000/0.7 \rceil = 1429$. Note that, the $ndp$ here is defined
to be the number of distinct length-$lss$ prefixes of the suffixes in
$SF$, which is equal to the size of the prefix set derived from $SF$
(after removing the repetitions).

Algorithm \ref{alg:hash} shows the pseudocode of building a hash table
based on $SF$. $SF$ is firstly partitioned into small suffix sets by
hashing: for each suffix $suf \in SF$, its prefix $suf^{+lss}$ is
hashed to an integer $i$ between 0 and $table\_size-1$ by the string
hash function , then $suf$ is associated with the $i$-th slot of the
hash table. After that, the suffixes whose length-$lss$ prefixes are
hashed to the same value are associated with the same slot of the hash
table. Then, to address the hash collisions, for each slot that is not
$NULL$, the associated suffixes form a small suffix set $SSF$, and a
new tree node is created adaptively based on the prefix set derived
from $SSF$, as shown in the \textsf{while} loop of Algorithm
\ref{alg:amt}. The newly created tree node is then associated with the
corresponding slot of the hash table. As a result, many tree nodes
with various types can be associated with one hash table.

% The suffixes whose length-$lss$ prefixes hashed to the same
% value $i$ are collected together associated with the $i$-th slot and
% forms a small suffix set. (Note that, we do not remove the prefixes of
% the suffixes when partitioning $SF$.) Then, to address the collisions,
% for each non-$NULL$ slot of the hash table, a tree node is built based
% on the small suffix set associated with that slot as stated
% before. Hence, many tree nodes with various structures can be
% incorporated in one hash table.

\begin{algorithm}
  \caption{Building a hash table}\scriptsize
  \label{alg:hash}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The suffix set $SF$ and the load factor $lf$. \\
    \ENSURE ~~\\
    The hash table.\\
    \STATE
    \STATE $ndp \leftarrow$ The number of distinct length-$lss$
    prefixes of suffixes in $SF$
    \STATE $table\_size \leftarrow \lceil ndp\,/\,lf \rceil$
    \STATE $hash\_table \leftarrow$ Create an array  of
    $table\_size$ pointers with each pointer initialized to $NULL$
    \STATE
    \FOR{each $suf \in SF$}
    \STATE $i \leftarrow Hash(suf^{+lss})$
    \STATE Associate $suf$ with $hash\_table[i]$
    \ENDFOR
    \STATE
    \FOR{$i \leftarrow 0$ to $table\_size - 1$}
    \IF{$hash\_table[i]\, \neq\, NULL$}
    \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
    \STATE $new\_node \leftarrow$ adaptively create a tree node from $SSF$, as shown in the \textsf{while} loop of Algorithm \ref{alg:amt}
    \STATE Associate $new\_node$ with $hash\_table[i]$
    \ENDIF
    \ENDFOR
    \STATE
    \RETURN $hash\_table$
  \end{algorithmic}
\end{algorithm}

In general, for a large pattern set, the root of the corresponding AMT
is usually a hash table, and the core function of the root can be
regarded as a ``filter'', which is able to filter out a great number
of positions of the text that are impossible to match any
pattern. Given a target string, the hash value of that string is
computed and used as the index of the hash table. If the corresponding
slot is $NULL$, which means the target string fails to match any key
in the hash table, the current matching round terminates and the
algorithm moves to the next position; otherwise, the process moves to
the tree node associated with that slot and compare the node with the
corresponding substring in the text.

The string hash function adopted can have a significant effect on the
performance of matching. In this work, for each matching task, the
hash function is selected randomly from a \textsf{hash function
  family} $H$, at the beginning of the matching phase. The hash
function family adopted in our implementation is the fast
\textsf{shift-add-xor} hash family proposed by Ramakrishna
\cite{Ramakrishna1997}, which is claimed to be both uniform and
universal. The form of the hash function family is shown in Algorithm
\ref{alg:hash fun}.

%  satisfied with the
% \textsf{uniformity}, \textsf{universality}, \textsf{applicability} and
% the \textsf{efficiency} properties

%  which should satisfy the following properties:

% \begin{itemize}
% \item \textbf{Uniformity.} If a hash function is uniform then the
% probability of an arbitrary key hashing to a given slot is
% $1/table\_size$, independent of the hash values of other keys. In
% practical terms, uniformity means that for a given load factor average
% access time is roughly constant, regardless of table size.

% \item {Universality.} A hash function family $H$ is universal
% if, for a given $table\_size$ and any pair of valid keys $k_1$ and
% $k_2$, the number of hash functions $h \in H$ such that $h(k_1) =
% h(k_2)$ is less than or equal to $|H|/table\_size$. That is, for a
% randomly-chosen hash function the probability that $k_1$ and $k_2$
% hash to the same value is less than or equal to $1/table\_size$.

% In practice universality means that, with high probability, a
% randomly-chosen hash function will perform well. For any hash function
% it is true that there exist sets of keys that all hash to the same
% value and no hash function is invulnerable to a deliberate attempt to
% identify such a set of keys. However, if a hash function family is
% universal and the functions in the family are uniform then it is
% guaranteed that the family cannot be subjected to such attack.

% \item {Applicability.} At a more pragmatic level, hash
% functions should be applicable in all circumstances where hashing
% might be used. A function that is limited to a few table sizes, can
% only hash strings of a certain length, is not as valuable as functions
% without such restrictions.

% \item {Efficiency}. The primary advantage of hashing as an
% access method is its speed: given $ndp$ keys and a table of $O(ndp)$
% size, the search time is $O(1)$, assuming a hash function with time
% complexity $O(1)$. Hash functions should also be small; in many
% applications there is little advantage to a function that is as large
% as the key set.

\begin{algorithm}
  \caption{The \textsf{shift-add-xor} hash family}\scriptsize
  \label{alg:hash fun}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The string $c_1c_2 \dots c_m$ and the $table\_size$.  \\
    \ENSURE ~~\\
    The hash value of $c_1c_2 \dots c_m$.
    \STATE
    \STATE $value \leftarrow seed$
    \FOR{$i \leftarrow 1$ to $m$}
    \STATE $value \leftarrow value \oplus (value << L + value >> R + c_i)$
    \ENDFOR
    \RETURN $value$ mod $table\_size$
  \end{algorithmic}
\end{algorithm}

Firstly, a random positive integer $seed$ is assigned to the initial
$value$ of the hash function. (Note that, different seeds give
different hash functions, consequently, a hash function family can be
defined by given different seeds.) Then the hash value is computed
gradually from each character of the input string, by using the
combinations of the \textsf{add, shift, xor} operators. In particular,
$\oplus$ is the \textsf{xor} operator, $value << \;L$ ($value >> \;R$)
means shift the $value$ to the left (right) $L$ ($R$) bits and $c_i$
is the ASCII value of the $i$-th character of the input
string. Through testing, we set $L=5$ and $R=2$ in our experiment,
which is able to provide greater likelihood of a uniform distribution
of hash values.

\section{Experimental Results}
\label{sec:experiments}

In this section, we evaluate the performance of \textsf{AAMPM}, and
compare it with other four algorithms: the \textsf{AC} and \textsf{WM}
algorithms, which are two classic ``baseline'' algorithms for MPM; the
\textsf{MASM} and \textsf{Pre-filter+AC} algorithms, which are two
state-of-the art MPM algorithms with good efficiency in practically
matching. All these algorithms are evaluated in two aspects: the
robustness of these algorithms under pattern sets with various $lsp$s
and the scalability of the algorithms under pattern sets with various
number of patterns.

\subsection{Simulation Settings}

The experiments are conducted on a PC with an Intel core i7 2.93GHz
CPU, 8GB of RAM and 1TB Disk Driver; the operating system is Windows 7
Professional (64-bits). All the testing algorithms are implemented in
C/C++ within the IDE of \emph{Code::Blocks}. The test data used in the
experiments is the real-world English text from the Pizza\;\&\;Chili
corpus. The patterns are extracted randomly from the text to form the
pattern sets.

Next, the parameter configuration in \textsf{AAMPM} in our experiment
are given. For the String Arrays, if the number of strings exceeds
\textbf{4}, the binary search is used to search the target string in
the key array; otherwise, the linear search is adopted. For the Hash
Tables, the load factor is set to \textbf{0.5}; the \emph{seed} of the
hash function is generated randomly in the range of
$\mathbf{1} \sim \mathbf{50}$; the shift values \emph{L} and \emph{R}
are set to \textbf{2} and \textbf{6} respectively. Once the $ndp$ is
lager than \textbf{100}, the Hash Table is built instead of the String
Array. These choices of parameters have been extensively tested on a
wide range of pattern sets, and are considered to be very efficient
for a typical match.

% The data sets include three kinds of data: the real-world English
% text and the DNA sequence from the Pizza\&Chili corpus, the random
% string which is generated artificially.

\subsection{Evaluation under various lsps}

As we've mentioned before, many MPM algorithms are sensitive to the
length of the patterns, particularly, the length of the shortest
pattern ($lsp$) in the pattern set. Therefore, it is necessary to
measure the performance of the \textsf{AAMPM} and compare it with the
other investigated algorithms under pattern sets with various
$lsp$s. In this evaluation, there are totally 9 pattern sets for
testing with $lsp$s ranging from 2 to 10, and every pattern set has a
fixed number of $10^5$ patterns. The size of text string is fixed to
200 MB. The characteristics of the pattern sets are shown in Table
\ref{tab:lsps}, which includes: the length of the shortest pattern
(LSP), the length of the longest pattern (LLP), the average length of
the patterns (ALP), the standard deviation of the pattern lengths
(SD), the total length of the patterns (TLP) and the number of
patterns in the pattern set (Count).

\begin{table}
  \centering
  \caption{The characteristics of pattern sets with various LSPs.}
  \scriptsize
  \label{tab:lsps}
  \begin{tabular}{rrrrrrr}
    \hline
    Pattern Set & LSP  & LLP  & ALP & SD & TLP & Count\\
    \hline
    $P_1$ & 2 & 50 & 25.9 & 14.1 & 2,599,020 & $10^5$\\
    $P_2$ & 3 & 50 & 26.5 & 13.9 & 2,646,762 & $10^5$\\
    $P_3$ & 4 & 50 & 27.0 & 13.6 & 2,704,091 & $10^5$\\
    $P_4$ & 5 & 50 & 27.6 & 13.2 & 2,745,545 & $10^5$\\
    $P_5$ & 6 & 50 & 27.9 & 13.0 & 2,793,178 & $10^5$\\
    $P_6$ & 7 & 50 & 28.4 & 12.7 & 2,843,580 & $10^5$\\
    $P_7$ & 8 & 50 & 29.0 & 12.4 & 2,903,343 & $10^5$\\
    $P_8$ & 9 & 50 & 29.5 & 12.1 & 2,948,372 & $10^5$\\
    $P_9$ &10 & 50 & 30.0 & 11.8 & 2,998,992 & $10^5$\\
    \hline
  \end{tabular}
\end{table}

% For universality, evaluation are performed independently on three
% different kinds of data: the English text, the DNA sequence and the
% random string. These three types of data have completely different
% alphabet and character combination. Therefore this evaluation can
% reflect the robustness of the algorithms for pattern sets with
% various features.

% The performance of the investigated algorithms are measured in
% preprocessing time and the matching time. The former is the time
% consumed by constructing the data structure in the preprocessing
% phase; the latter is used for matching with the text string in the
% matching phase. Usually, most of the algorithms mainly focus on the
% matching time, however, the preprocessing time is also significant
% factor, since a very short preprocessing time means the algorithm
% allows the pattern set to be updated dynamically.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{./eps/lsp}
  \caption{Matching times for various lsps.}
  \label{fig:lsp}
\end{figure}

Figure \ref{fig:lsp} presents the mean matching time (in seconds) used
by these algorithms based on 5 independent runs.  In general, the
\textsf{AC} algorithm is not affected much by the changes in $lsp$.
However, the DFA built by this algorithm consumes a huge amount of
memory. What's worse is that, the frequent, unpredictable
state/failure transitions will lead to a lot of cache misses during
matching, and these results in the low performance of \textsf{AC}. The
\textsf{WM} algorithm outperforms \textsf{AC} on the pattern sets
whose $lsp$ is larger than 2, even so, for the pattern sets with small
$lsp$, the performance of \textsf{WM} degrades dramatically. This is
due to the ``skip strategy'' of \textsf{WM} algorithm that does not
work well for the pattern sets with small $lsp$s, which means most of
the positions in the text need to be checked by the HASH table of
\textsf{WM}, and this takes a lot of time. The \textsf{Pre-filter+AC}
algorithm outperforms all other algorithms (except \textsf{AAMPM}) for
pattern sets whose $lsp$ is larger than 4. Similarly, this algorithm
also uses a skip strategy: once a position of the text is filtered out
by the Pre-filter, at most the following $lsp-1$ positions can be
skipped over. Consequently, for pattern sets with small $lsp$, this
algorithm can not skip much in the text, which will seriously affect
its performance. In contrast, the \textsf{MASM} algorithm performs
well for small $lsp$ ($lsp \leq 4$). This algorithm first compacts the
pattern set by a prefix tree: if a pattern $A$ is a prefix of another
pattern $B$, $A$ can be merged into $B$. Then the algorithm builds a
binary search tree for the compacted pattern set based on
lexicographical order. Comparing with the long patterns, the short
ones are more likely to be prefixes of others, and thus, more likely
to be eliminated by compacting. Thus, pattern sets with small $lsp$
are well compressed, which will improve both time and space efficiency
of \textsf{MASM} in the matching phase.

From Figure \ref{fig:lsp} we can see that, \textsf{AAMPM} outperforms
all other investigated algorithms on every $lsp$. Comparing with
\textsf{AC}, the matching time is reduced by $85\%$ in average for all
$lsp$s; even comparing with the fast \textsf{Pre-filter+AC} algorithm,
the matching time is reduced by $10\% \sim 20\%$ for medium $lsp$s
($lsp \geq 4$) and by $70\%$ for small $lsp$s ($lsp < 4$). As
mentioned before, this is mainly due to the adaptivity of the nodes of
AMT, which enables the tree nodes as efficient and compact as
possible. Therefore, no matter what the $lsp$s of the pattern sets
are, the corresponding AMT is able to keep high search efficiency as
well as low memory requirement in the matching phase. Owing to this,
the \textsf{AAMPM} has the best robustness for all of the testing
pattern sets. The statistics about node types of corresponding AMTs
are shown in table \ref{tab:node types}. The Single Char and Single
String types in the table are actually the Map 4 and String Array
types which contain only one element, respectively. Obviously, as the
$lsp$ of the pattern set changes, the number of nodes of the each type
in the AMT changes accordingly, which reflects the adaptivity of AMT.

Moreover, the performance of \textsf{AAMPM} is very stable and
reliable. In particular, once the length of the text and number of
patterns are fixed, the matching time changes little for various
$lsp$s. As shown in Figure \ref{fig:lsp}, the matching time of
\textsf{AAMPM} is always about 10 seconds for a text of 200MB and a
pattern set with $10^5$ patterns; for $lsp$s ranging from $2$ to $10$,
the change in the matching time is less than 2 seconds. In fact, as
the $lsp$ increases, the average length of the paths from the root to
the leaves in AMT will increase slightly. Accordingly, in the matching
phase, the matching paths for some text positions may get a little
longer, which might slightly slow down the matching speed.

% Since these volumes are all fixed in this evaluation, the matching
% time is nearly the same under all lsps.

\begin{table}[!htp]
  \centering
  \caption{The statistics about the AMTs under various lsps}
  \scriptsize
  \label{tab:node types}
  \begin{tabular}{rrrrrrrrrr}
 \hline
 Lsp &
 Single Char &
 Map 4 &
 Map 16 &
 Map 48 &
 Map 256 &
 Single String &
 String Array   &
 Hash Table &
 Total\\
 \hline
 2  & 2,464 & 2,096 & 663 & 133 & 0 & 63,274 &  21,627 & 10 & 90,267\\
 3  & 2,379 & 1,636 & 385 & 90  & 0 & 64,701 &  22,551 & 10 & 91,752\\
 4  & 2,273 & 1,329 & 201 & 57  & 0 & 66,162 &  22,736 &  1 & 92,759\\
 5  & 2,045 & 1,104 & 112 & 45  & 0 & 68,152 &  22,048 &  1 & 93,507\\
 6  & 1,758 &   899 &  52 & 34  & 0 & 70,179 &  20,818 &  1 & 93,741\\
 7  & 1,560 &   807 &  29 & 33  & 0 & 72,284 &  19,280 &  1 & 93,994\\
 8  & 1,515 &   803 &  20 & 31  & 0 & 73,447 &  18,274 &  1 & 94,091\\
 9  & 1,441 &   788 &  24 & 30  & 0 & 74,584 &  17,120 &  1 & 93,988\\
10  & 1,361 &   794 &  24 & 29  & 0 & 75,094 &  16,427 &  1 & 93,730\\
\hline
  \end{tabular}
\end{table}

\subsection{Evaluation under various numbers of patterns}

In this section, we evaluate the scalability of the investigated
algorithms by testing them under pattern sets with various numbers of
patterns. As before, the size of the text is fixed to 200MB, and there
are two groups of pattern sets for testing --- the small group and the
large group. The small group contains 9 pattern sets, with the sizes
(number of patterns) increasing from $1 \times 10^5$ to
$9 \times 10^5$ in steps of $10^5$, while the large group contains 10
pattern sets, with the sizes increasing from $10^6$ to $10^7$ in steps
of $10^6$. The range of the pattern length of each pattern set is
fixed to $5 \sim 50$.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{./eps/small_group}
  \caption{Matching times for the small group.}
  \label{fig:small_group}
\end{figure}

For the small group, the mean matching times of the investigated
algorithms under 5 independent runs are shown in Figure
\ref{fig:small_group}. The experimental results indicate that, the
performance of the \textsf{AC} algorithm is relative stable (but not
high) as the number of patterns growing, but it can not deal with
pattern sets whose size is larger than $7 \times 10^5$ in this testing
due to lack of memory. Although the \textsf{WM} algorithm performs
better than \textsf{AC}, it is less stable, for instance, the matching
time only rises about $1s$ as the number of patterns increasing from
$2 \times 10^5$ to $3 \times 10^5$, but when the number of patterns
increases from $8 \times 10^5$ to $9 \times 10^5$, the matching time
rises up to $9s$. Thus, we can not estimate the matching time of
\textsf{WM} based on the size of the pattern set. The
\textsf{Pre-filter+AC} performs well as the number of patterns
growing, but its matching time is also unpredictable, e.g. the
matching times are nearly the same as the number of patterns
increasing from $4 \times 10^5$ to $5 \times 10^5$. The instability of
\textsf{WM} and \textsf{Pre-filter+AC} is mainly due to that: the
effect of the filters used by these two algorithms highly depends on
the contents of the text and patterns themselves, for some pattern
sets whose patterns occurs frequently in the text, the effect of the
filters degrades. On the other hand, as the number of patterns grows,
the matching time of \textsf{MASM} grows more slowly than that of the
\textsf{Pre-filter+AC}, which is due to that the matching time of
\textsf{MASM} mainly relies on the depth of the pipelinded binary
search tree and that depth grows very slow as the number of patterns
increasing.

% For the \textsf{MASM} algorithm, its
% performance is more stable than the \textsf{Pre-filter+AC} algorithm.
% This is because the performance of \textsf{MASM} mainly relies on the
% depth of the pipelined binary search tree, which  as the
% number of patterns increases.

\begin{table}[!htp]
  \scriptsize
  \caption{The statistics about the AMTs for the small group}
  \label{tab:small}
  \begin{tabular}{rrrrrrrrrr}
 \hline
 Size &
 Single Char &
 Map 4 &
 Map 16 &
 Map 48 &
 Map 256 &
 Single String &
 String Array   &
 Hash Table &
 Total\\
\hline
$1 \times 10^5$  &  2,000 &  1,006 &    72 &  18 & 0 &  68,268 &  21,971 & 103 &  93,438 \\
$2 \times 10^5$ &  4,628 &  2,808 &   307 &  42 & 0 & 130,440 &  46,514 & 244 & 184,983 \\
$3 \times 10^5$ &  7,414 &  4,858 &   574 &  84 & 0 & 190,653 &  71,757 & 403 & 275,746 \\
$4 \times 10^5$ & 10,555 &  7,282 &   946 & 139 & 0 & 247,656 &  97,967 & 544 & 365,089 \\
$5 \times 10^5$ & 13,703 & 10,651 & 1,503 & 238 & 4 & 302,350 & 124,528 &  17 & 452,994 \\
$6 \times 10^5$ & 17,335 & 13,536 & 1,954 & 298 & 0 & 356,644 & 151,435 &  31 & 531,233 \\
$7 \times 10^5$ & 21,080 & 16,872 & 2,405 & 388 & 4 & 408,165 & 179,621 &  35 & 628,570 \\
$8 \times 10^5$ & 24,357 & 20,094 & 2,977 & 436 & 3 & 457,674 & 208,426 &  37 & 714,004 \\
$9 \times 10^5$ & 28,356 & 23,924 & 3,441 & 513 & 9 & 504,779 & 238,632 &  42 & 799,696 \\
\hline
  \end{tabular}
\end{table}

Among all these algorithms, the \textsf{AAMPM} is the most efficient
as well as stable one. The high performance of \textsf{AAMPM} is
mainly due to the \emph{root} node of AMT, which is almost always the
Hash Table as the number of patterns grows. As mentioned before, the
root plays the role of a ``filter'', by which a large number of
positions of the text that are impossible to match with any pattern
can be quickly filtered out. Moreover, the increasing in the number of
patterns mainly leads to the growing of the width rather than the
depth of AMT. Therefore, for each position of the text, the checking
time changes slightly. From the experimental results, we can even give
a rough estimate on the matching time based on the size of pattern set
as follows: given the text of 200 MB, an increase of $10^5$ in the
number of patterns will lead to roughly $1$ more second taken in the
matching time. The statistics about the node types of the
corresponding AMTs for the small group are shown in Table
\ref{tab:small}. We can see that an increase of $10^5$ in the number
of patterns will yield about $9 \times 10^4$ tree nodes.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{./eps/large_group}
  \caption{Matching times for the large group.}
  \label{fig:large_group}
\end{figure}

For the large group, the mean matching times of the investigated
algorithms are shown in Figure \ref{fig:large_group}.  From the
results we can see that, as the number of patterns grows from $10^6$
to $10^7$, the increases in the matching time of the investigated
algorithms are: $410\%$ (\textsf{WM}), $374\%$
(\textsf{Pre-filter+AC}), $238\%$ (\textsf{MASM}), $112\%$
(\textsf{AAMPM}) respectively. For every increase of $10^6$ in the
number of patterns, the mean increment in the matching time of the
investigated algorithms are: $23.7s$ (\textsf{WM}), $17.0s$
(\textsf{Pre-filter+AC}), $12.3s$ (\textsf{MASM}), $3.5s$
(\textsf{AAMPM}) respectively. From the results we can see that,
\textsf{Pre-filter+AC} and \textsf{WM} perform not well for large
pattern sets. This is because, as the number of patterns grows, the
chances for every position of the text to successfully match a pattern
increases, which will reduce the effect of the filters of these
algorithms and results in performance degradation. The \textsf{MASM}
algorithm outperforms \textsf{Pre-filter+AC} for pattern sets whose
size are larger than $3 \times 10^6$, which is due to its pattern set
compression strategy and the good scalability of its pipelinded binary
search tree.

\begin{table}[!htp]
  \caption{The statistics about the AMTs for the large group}
  \scriptsize
  \label{tab:large_group}
  \begin{tabular}{rrrrrrrrrr}
 \hline
 Size &
 Single Char &
 Map 4 &
 Map 16 &
 Map 48 &
 Map 256 &
 Single String &
 String Array   &
 Hash Table &
 Total\\
\hline
$1 \times 10^6$ &  38,935 &   27,428  &   6,468 &     851   &	 4 &    588,343	 &    240,886 &  1,027 &    903,942  \\
$2 \times 10^6$ &  85,900 &   68,973  &  17,084 &   2,141   &	20 &  1,091,527	 &    496,001 &  2,015 &  1,763,661  \\
$3 \times 10^6$ & 136,054 &  117,527  &  28,092 &   3,410   &	17 &  1,547,659	 &    764,359 &  2,749 &  2,599,867  \\
$4 \times 10^6$ & 189,926 &  171,155  &  40,328 &   4,716   &	23 &  1,966,326	 &  1,045,558 &  3,450 &  3,421,482  \\
$5 \times 10^6$ & 247,707 &  230,163  &  83,043 &   5,989   &  38 &  2,354,308	 &  1,332,896 &  3,885 &  4,228,029  \\
$6 \times 10^6$ & 304,863 &  293,591  &  65,475 &   7,169   &	49 &  2,706,094	 &  1,625,261 &  4,379 &  5,006,881  \\
$7 \times 10^6$ & 366,861 &  361,695  &  77,899 &   8,434   &	53 &  3,030,673	 &  1,925,027 &  4,733 &  5,775,380  \\
$8 \times 10^6$ & 429,121 &  433,708  &  90,280 &   9,660   &	62 &  3,336,765	 &  2,226,879 &  5,070 &  6,531,545  \\
$9 \times 10^6$ & 494,278 &  509,992  & 102,402 &  10,833   &	72 &  3,623,407	 &  2,537,413 &  5,224 &  7,283,621  \\
$1 \times 10^7$ & 558,241 &  591,455  & 115,012 &  11,922   &	79 &  3,986,683	 &  2,847,277 &  5,505 &  8,026,174  \\
\hline
\end{tabular}
\end{table}

On the other hand, among all the algorithms, \textsf{AAMPM} is the
most efficient algorithm for large pattern sets. An increase of $10^6$
in the number of patterns, only require 3 more seconds to match, this
is mainly due to the good scalability of the AMT which enables the
matching time grows very slow as the number of patterns explodes. The
statistics about the AMTs for the large group are shown in Table
\ref{tab:large_group}. Every $10^6$ increase in the number of patterns
will increase only about $8 \times 10^5$ tree nodes.

\section{Conclusion and Future Works}
\label{sec:conclusion}

In this paper, we propose an Adaptive Architecture for Multi-Pattern
Matching (\textsf{AAMPM}). The \textsf{AAMPM} used a data structure
called Adaptive Matching Tree (AMT) which can be constructed to fit
the feature of the given pattern set. Using the AMT to match with the
text can improve the robustness of \textsf{AAMPM} for pattern sets
with various $lsp$s. Moreover, owing to the scalability and
compactness of AMT, \textsf{AAMPM} offers a good support for
large-scale pattern sets. In the future, we will try to design more
efficient inner structures of the tree nodes; furthermore, since
\textsf{AAMPM} needs to check every position of the text string, we
will further improve this by designing a ``skip scheme'' for
\textsf{AAMPM}.

\section{Acknowledgments}

This work is supported by National Natural Science Foundation of China
(No.61472297).

\bibliography{./DM}

\end{document}

% which means the suffix set is actually the
% original whole pattern set)

% \begin{tikzpicture}[scale=1.8]

% %\filldraw[fill=red, draw=green] (0,0) circle [ radius=1cm];
% \shade[left color=red, right color=black] (0,0) rectangle (1,1);
% \shadedraw[ball color=yellow, draw=balck] (1.5,0.5) circle [radius=0.5];
% \draw (-1.5,0)--(1.5,0);
% \draw (0,-1.5)--(0,1.5);
% \draw[rotate=45] (0,0) rectangle (0.5,0.5);
% \draw (0,0) rectangle (1,1);
% \fill[green!20!white] (0,0) -- (1cm,0) -- arc[start angle=0, end angle=30, radius=1cm]--(0cm,0cm);
% \draw (-1,-1) rectangle (-0.5,-0.5);
% \draw (3mm,0mm) arc [start angle=45, end angle=110, radiu
% s=3mm];$PF$$PF$$PF$
% \end{tikzpicture}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2016-08-04 Engine.tex
1.修改Verifacion部分(完成);2.修改自适应构造节点部分(完成)

@@
   step 2.
-\item Divide $SF$ by putting together all its suffixes who have the
-  same prefix removed, to form a sub-suffix-set. Associate each
-  sub-suffix-set with the corresponding prefix in the tree \emph{node}.
+\item Divide $SF$ by putting together all the suffixes with same
+  prefix removed, to form a sub-suffix-set. Associate each
+  sub-suffix-set with the corresponding prefix in the tree
+  \emph{node}.
 \item For each newly created sub-suffix-set in step 3, repeat the same
@@
 text has been detected by the filter module, the verification module
-checks that position for real pattern occurrences. In particular, for
+checks that position for real pattern occurrences. Specifically, for
 such a suspicious position $i$, the engine searches a sequence of
@@
 mismatch or the searching goes beyond the leaves of AMT, the engine
-forwards to the next position of the text and invokes the filter.
-
-The pseudocode of verifying is shown in Algorithm
+immediately forwards to the next position $i+1$ and invokes the
+filter.
+
+The pseudocode of the verification procedure is shown in Algorithm
 \ref{alg:matching}. Suppose $i$ is a suspicious position in the
@@
     \ENSURE ~~\\
-    The patterns start at $i$ (if any)
+    The patterns (if any) start at $i$ 
     \STATE
@@
     \IF{$key$ is marked as a pattern end}
-    \STATE The pattern $T[i,\,m\_len]$ is found at position $i$
+    \STATE Report that the pattern $T[i,\,m\_len]$ is found at position $i$
     \ENDIF
@@
   \includegraphics[width=0.75\textwidth]{./eps/match}
-  \caption{The matching round that searches patterns starting at
-    position $i$ of the text.}
+  \caption{The verification procedure for the position $i$ in the
+    text.}
   \label{fig:matching}
@@
 the verification for position $i$ of a given text string $T$, using
-the AMT built in section \ref{subsec:amt}. The matching round starts
+the AMT built in section \ref{subsec:amt}. The verification starts
 from the root of AMT: according to $key\_len(root)=2$, the same length
 sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
-taken to check whether it's one of the keys in root. The result is
-that: $aa \in root$, and also $aa$ is marked as a pattern
-end. Therefore the pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is
-found at position $i$. Then the matching transfers to $node_1$, which
-is the child node of $root.aa$.
+taken to check whether it's one of the keys in root. The result is:
+$aa \in root$, and $aa$ is also marked as a pattern end. Therefore the
+pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is found at position
+$i$. Then the verification transfers to $node_1$, which is the child
+node of $root.aa$.
 
 At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
-$T[i+2,\,6]=e^6$, which appears following $T[i,\,2]$, is trying to
-match with some key in $node_1$. The result is that: $e^6 \in node_1$
-but it is not marked as a pattern end. Then the matching simply
-transfers to $node_5$, which is the child of $node_1.e^6$.
+$T[i+2,\,6]=e^6$, which follows $T[i,\,2]$, is trying to match with
+some key in $node_1$. The result is that: $e^6 \in node_1$ but it is
+not a pattern end. Then the verification simply transfers to $node_5$,
+which is the child of $node_1.e^6$.
 
@@
 $T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
-$i$. Then the matching goes to the child of $node_5.u^5$, i.e.
+$i$. Then the verification goes to the child of $node_5.u^5$, i.e.
 $node_{10}$.
 
-At $node_{10}$, since $T[i+13,\,4]=sscc \notin node_{10}$, the current
-matching round for position $i$ terminates. The algorithm restarts a
-new matching round for the next position $i+1$. Once all the positions
-of the text have been checked, the whole algorithm terminates.
-
-In our approach, each matching round actually corresponds to a
-\textsf{matching path} in the AMT, whose tree nodes have been compared
-with the text in the former matching process. In particular, the
-matching path of the given example is:
+At $node_{10}$, since $T[i+13,\,4]=sscc \notin node_{10}$, the
+verification for position $i$ terminates. And next, the engine will
+forward to position $i+1$ and invoke the filter module for that
+position.
+
+From above it can be seen that, each verification procedure actually
+corresponds to a \emph{verification path} in the AMT, whose tree nodes
+have been compared with the text in the former process. In particular,
+the verification path of the given example is:
 $root \rightarrow node_1 \rightarrow node_5 \rightarrow node_{10}$,
@@
 As stated in section \ref{subsec:amt}, each node of AMT has a specific
-structure to hold the prefixes of a prefix set as the keys. The type
-of the node structure is chosen adaptively according to the features
-of the prefix set. Since all the keys in the prefix set have the same
-length, the features of the prefix set can mainly be characterized by
-two parameters: the \textsf{length} and \textsf{number} of the keys in
-the prefix set. These two parameters are respectively symbolized by
-$lss$ and $ndp$ in Section \ref{subsec:amt}.
-
-In this work, three kinds of structures, i.e. \textsf{character map},
-\textsf{string array} and \textsf{hash table} can be adopted for
-prefix sets with different $lss$ and $ndp$ combinations. Next, the
-detailed descriptions of them will be presented.
+index structure to hold the prefixes of a prefix set as the keys. The
+type of the index structure is chosen adaptively according to the
+features of the prefix set. Since all the keys in the prefix set have
+the same length, the features of the prefix set can mainly be
+characterized by two values: the \emph{length} and \emph{number} of
+the keys in the prefix set. These two values are respectively
+symbolized by $lss$ and $ndp$ in Section \ref{subsec:amt}.
+
+In this work, three different kinds of structures,
+i.e. \emph{character map}, \emph{string array} and \emph{hash table}
+can be adopted for prefix sets with different $lss$ and $ndp$
+combinations. Next, the detailed descriptions of these structures will
+be presented.
 
@@
 Given a prefix set, if the length of keys is equal to 1 ($lss=1$),
-i.e. each key in the prefix set is just a single character, we adopt
-the space-efficient \textsf{character map} structure, which was
-proposed by Leis \cite{Leis2013}, as the tree node. There are four
+i.e. each key in the prefix set is just a single character, the
+space-efficient \emph{character map} structure, which was proposed by
+Leis \cite{Leis2013}, will be adopted as the tree node. There are four
 sub-types of character maps with different capacities for different
@@
 pairs, the key part and the child pointer part are stored in the
-separate arrays, which is able to keep the node information compact
+separate arrays, which is able to keep the node structure compact
 while supporting efficient search.
@@
   arrays, and the keys are sorted according to their ACSII
-  values. Once the target character is found in the key array, its
-  child pointer can be located through the same position in the
-  pointer array. Figure \ref{fig:character map} (a) shows a Map 4
-  structure with three keys: $a$, $b$ and $c$, where the triangles
+  values. Once the target string (character) is found in the key
+  array, its child pointer can be located through the same position in
+  the pointer array. Figure \ref{fig:character map} (a) shows a Map 4
+  structure with three keys: $f$, $n$ and $p$, where the triangles
   with the keys inside represent the corresponding child nodes.
@@
   retrieved efficiently by a binary search in the key array. Figure
-  \ref{fig:character map} (b) shows a Map 16 structure with 14 keys:
-  $a \sim n$.
+  \ref{fig:character map} (b) shows a Map 16 structure with 14 keys.
 
@@
   expensive. Therefore, maps with more than 16 (but less than 49) keys
-  do not store the keys explicitly. Instead, a 256-element
-  \textsf{index array} is used, which can be directly indexed by the
-  ASCII value of the target character. This array stores only the
-  \textsf{array indexes} (small inters in the range of $[0,47]$) of
-  another pointer array that contains up to 48 child pointers. In this
-  way, the storage space can be saved comparing with storing pointers
-  directly, because each array index only requires one byte. Figure
-  \ref{fig:character map} (c) shows a Map 48 structure, where the
-  ASCII values of $a$, $b$ and $c$ are 97, 98 and 99 respectively.
+  do not store the keys explicitly. Instead, a 256-element \emph{index
+    array} is used, which can be directly indexed by the ASCII value
+  of the target character. This array stores only the array indexes
+  (small inters in the range of $[0,47]$) of another pointer array
+  that contains up to 48 child pointers. In this way, the storage
+  space can be saved comparing with storing pointers directly, because
+  each array index only requires one byte. Figure \ref{fig:character
+    map} (c) shows a Map 48 structure, where the ASCII values of $a$,
+  $b$ and $c$ are 97, 98 and 99 respectively.
 
@@
 
-For the sake of clarity, the pseudocode of searching in a node, whose
-type is character map, is given in Algorithm \ref{alg:character map}.
+The pseudocode of searching in a node, whose type is character map, is
+given in Algorithm \ref{alg:character map}.
 
@@
     \ENDFOR
-    \RETURN $NULL$
+    \STATE Report a mismatch.
     \ENDCASE
@@
     \ENDWHILE
-    \RETURN $NULL$
+    \STATE Report a mismatch.
     \ENDCASE
@@
     \ELSE
-    \RETURN $NULL$
+    \STATE Report a mismatch.
     \ENDIF
@@
 and the number of keys is not greater than 100 ($ndp \leq 100$), the
-\textsf{string array} structure is constructed as a tree node. Similar
-to the character map, the keys are stored in lexicographical order in
-a separate key array of $ndp \times lss$ bytes, in which each key
-takes $lss$ bytes. The child pointers are stored at the corresponding
-positions in another pointer array of $8 \times ndp$ bytes, where each
-pointer takes 8 bytes in a typical x86\_64 architecture. Figure
+\emph{string array} structure is constructed as a tree node. Similar
+to the Map 4 and Map 16 structures, the keys are stored in
+lexicographical order in a separate key array of $ndp \times lss$
+bytes, in which each key takes $lss$ bytes. The child pointers are
+stored at the corresponding positions in another pointer array. Figure
 \ref{fig:string array} illustrates a string array structure holding
-there keys: $aaa$, $bbb$ and $ccc$. The key and pointer arrays occupy
-9 and 24 bytes respectively.
+three keys: $aaa$, $bbb$ and $ccc$.
 
@@
 use the notation $A \prec B$ to denote that string $A$ is
-\textsf{lexicographically smaller} than string $B$. For the string
-array whose number of keys is less than 5, the target string is
-compared sequentially with the keys in the key array. If the target
-string matched some key, return the child pointer at the corresponding
-position in the pointer array; otherwise, return $NULL$. On the other
-hand, if the number of keys is greater than 4, the target string is
-searched by a binary search routine from the middle element of the key
-array.
+\emph{lexicographically smaller} than string $B$. For the string array
+whose number of keys is less than 5, the target string is compared
+sequentially with the keys in the key array. If the target string
+matched some key, return the child pointer at the corresponding
+position in the pointer array; otherwise, report a mismatch. On the
+other hand, if the number of keys is greater than 4, the target string
+is searched by a binary search routine from the middle element of the
+key array.
 
@@
     \ELSE
-    \RETURN $NULL$
+    \STATE Report a mismatch
     \ENDIF
@@
     \ENDWHILE
-    \RETURN $NULL$
+    \STATE Report a mismatch.
     \ENDIF
@@
 inefficient even using a binary search. In this case, a more fast (but
-heavy) data structure --- \textsf{hash table} is adopted to deal with
-large number of keys. In this work, a hash table is an array of child
-pointers with each pointer initialized to $NULL$, and we utilize a
-\textsf{string hash function} which transforms a string to a positive
-integer. It is worth noting that, the procedure of building a hash
-table is directly based on the suffix set rather than the prefix set
-which is the basis of building other structures.
+heavy) data structure --- \emph{hash table} is adopted to deal with
+large number of keys. It is worth noting that, the procedure of
+building a hash table is directly based on the suffix set from which
+the prefix set is formed rather than the prefix set which is the basis
+of building other node structures. In this work, a hash table is an
+array of child pointers with each pointer initialized to $NULL$, and
+we also utilize a \emph{string hash function} which transforms a
+string to a positive integer.
 
@@
 In particular, given a suffix set $SF$, the size of the hash table
-(denoted by $table\_size$) is determined by $ndp$ and a given
-\textsf{load factor} $lf$ (ratio of $ndp$ to $table\_size$), i.e.
+(denoted by $table\_size$) is determined by $ndp$ and a given load
+factor $lf$ (ratio of $ndp$ to $table\_size$), i.e.
 $table\_size = \lceil ndp\,/\,lf \rceil$. For example, with the $ndp$
@@
 hash function , then $suf$ is associated with the $i$-th slot of the
-hash table. After that, the suffixes whose length-$lss$ prefixes are
-hashed to the same value are associated with the same slot of the hash
-table. Then, to address the hash collisions, for each slot that is not
-$NULL$, the associated suffixes form a small suffix set $SSF$, and a
-new tree node is created adaptively based on the prefix set derived
-from $SSF$, as shown in the \textsf{while} loop of Algorithm
-\ref{alg:amt}. The newly created tree node is then associated with the
-corresponding slot of the hash table. As a result, many tree nodes
-with various types can be associated with one hash table.
+hash table. After that, the suffixes whose length-$lss$ prefixes
+hashing to the same value are associated with the same slot of the
+hash table. Then, to address the hash collisions, for each slot that
+is not $NULL$, the associated suffixes form a small suffix set $SSF$,
+and a new tree node is created adaptively based on the prefix set
+derived from $SSF$, as we have shown in the \textbf{while} loop of
+Algorithm \ref{alg:amt}. The newly created tree node is then
+associated with the corresponding slot of the hash table. As a result,
+many tree nodes with various types can be associated within one hash
+table.
 
@@
     \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
-    \STATE $new\_node \leftarrow$ adaptively create a tree node from $SSF$, as shown in the \textsf{while} loop of Algorithm \ref{alg:amt}
+    \STATE $new\_node \leftarrow$ adaptively create a tree node from
+    $SSF$, as shown in the \textbf{while} loop of Algorithm \ref{alg:amt}
     \STATE Associate $new\_node$ with $hash\_table[i]$
@@
 
-In general, for a large pattern set, the root of the corresponding AMT
-is usually a hash table, and the core function of the root can be
-regarded as a ``filter'', which is able to filter out a great number
-of positions of the text that are impossible to match any
-pattern. Given a target string, the hash value of that string is
-computed and used as the index of the hash table. If the corresponding
-slot is $NULL$, which means the target string fails to match any key
-in the hash table, the current matching round terminates and the
-algorithm moves to the next position; otherwise, the process moves to
-the tree node associated with that slot and compare the node with the
+Given a target string of length $lss$, the hash value of that string
+is computed and used as the index of the hash table. If the
+corresponding slot is $NULL$, which means the target string fails to
+match any key in the hash table, the verification terminates and the
+engine moves to the next position; otherwise, the process goes to the
+tree node associated with that slot and compares the node with the
 corresponding substring in the text.
@@
 The string hash function adopted can have a significant effect on the
-performance of matching. In this work, for each matching task, the
-hash function is selected randomly from a \textsf{hash function
-  family} $H$, at the beginning of the matching phase. The hash
-function family adopted in our implementation is the fast
-\textsf{shift-add-xor} hash family proposed by Ramakrishna
-\cite{Ramakrishna1997}, which is claimed to be both uniform and
-universal. The form of the hash function family is shown in Algorithm
-\ref{alg:hash fun}.
+performance of verifying. In our implementation, for each matching
+task, the hash function is selected randomly from a \emph{hash
+  function family} $H$. The hash function family adopted in our
+implementation is the fast \emph{shift-add-xor} hash family proposed
+by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
+uniform and universal. The form of the hash function family is shown
+in Algorithm \ref{alg:hash fun}.
 

### 2016-08-05 Engine.tex
再次修改 verification 和 自适应节点部分

@@
 
-As stated in the filtering phase, once a suspicious position in the
-text has been detected by the filter module, the verification module
-checks that position for real pattern occurrences. Specifically, for
-such a suspicious position $i$, the engine searches a sequence of
-substrings of the text, where the first substring starts at $i$, in
-the corresponding nodes in AMT from the root. If the text successfully
-matched a key that is marked as a pattern end in some node, a pattern
-is declared to be found at position $i$. However, if there is a
-mismatch or the searching goes beyond the leaves of AMT, the engine
-immediately forwards to the next position $i+1$ and invokes the
-filter.
+As stated in the filter module, once a suspicious position in the text
+has been detected, the verification module checks that position for
+real pattern occurrences. Specifically, for such a suspicious position
+$i$, the engine searches a sequence of substrings of the text, where
+the first substring starts at $i$, in the corresponding nodes of AMT
+from the root. If any substring successfully matched a key that is
+marked as a pattern end in some node, a pattern is declared to be
+found at position $i$. However, if there is a mismatch or the
+searching goes beyond the leaves of AMT, the engine immediately
+forwards to the next position $i+1$ and invokes the filter again.
 
 The pseudocode of the verification procedure is shown in Algorithm
-\ref{alg:matching}. Suppose $i$ is a suspicious position in the
-text. The $m\_len$ is the total length of the successfully matched
-sub-strings of the text. The $node$ points to the current matching
-node in the AMT. In addition, since all the keys in a node have the
-same length, the notation $key\_len(node)$ is used to denote the
-length of the keys in $node$.
+\ref{alg:matching}. Suppose $i$ is a suspicious position of the text
+detected by the filter module. The variable $m\_len$ is the total
+length of the sub-strings of the text who have matched with keys in
+AMT nodes. The variable $node$ points to the current searching node in
+the AMT. In addition, since all the keys in a node have the same
+length, the notation $key\_len(node)$ is used to denote the length of
+the keys in $node$.
 
@@
 of the key. At the same time, if the matched $key$ is also marked as a
-pattern end, the engine will report that a pattern, which is
-$T[i,\,m\_len]$, is found at position $i$. Then the matching transfers
-to the child of $node.key$ and makes that child node to be the current
-node. Once there is a mismatch or the current node goes beyond the
-leaves of AMT (i.e.  $node = NULL$), the verification terminates, and
-the engine forwards to the next position $i+1$.
+pattern end, the verification module will report that a pattern,
+i.e. $T[i,\,m\_len]$, is found at position $i$. Then the checking
+transfers to the child of $node.key$ and makes that child node to be
+the current node. Once there is a mismatch or the current node goes
+beyond the leaves of AMT (i.e.  $node = NULL$), the checking
+terminates, and the engine forwards to the next position $i+1$.
 
@@
 Next, an example is given in figure \ref{fig:matching} to illuminate
-the verification for position $i$ of a given text string $T$, using
-the AMT built in section \ref{subsec:amt}. The verification starts
-from the root of AMT: according to $key\_len(root)=2$, the same length
-sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
-taken to check whether it's one of the keys in root. The result is:
-$aa \in root$, and $aa$ is also marked as a pattern end. Therefore the
-pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is found at position
-$i$. Then the verification transfers to $node_1$, which is the child
-node of $root.aa$.
+the verification for a suspicious position $i$ of a given text string
+$T$, using the AMT built in section \ref{subsec:amt}. The verification
+starts from the root of AMT: according to $key\_len(root)=2$, the same
+length sub-string starting at position $i$ of $T$, which is
+$T[i,\,2]=aa$, is taken to check whether it's one of the keys in
+root. The result is: $aa \in root$, and $aa$ is also marked as a
+pattern end. Therefore the pattern $T[i,\,2]=aa$ ($p_6$ in $P$) is
+found at position $i$. Then the checking transfers to $node_1$, which
+is the child node of $root.aa$.
 
@@
 some key in $node_1$. The result is that: $e^6 \in node_1$ but it is
-not a pattern end. Then the verification simply transfers to $node_5$,
+not a pattern end. Then the checking simply transfers to $node_5$,
 which is the child of $node_1.e^6$.
@@
 $u^5$ is marked as a pattern end, another pattern
-$T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
-$i$. Then the verification goes to the child of $node_5.u^5$, i.e.
-$node_{10}$.
+$T[i,\,13]=a^2e^6u^5$ ($p_4$ in $P$) is found at position $i$. Then
+the checking goes to the child of $node_5.u^5$, i.e.  $node_{10}$.
 
@@
   \caption{The four sub-types of character maps. The triangles
-    represent the corresponding child nodes.}
+    represent the corresponding child nodes of the keys.}
   \label{fig:character map}
@@
 character maps which are named according to their maximum
-capacity. Instead of using an array of (\emph{key, child pointer})
+capacity. Instead of using one array of (\emph{key, child pointer})
 pairs, the key part and the child pointer part are stored in the
@@
   arrays, and the keys are sorted according to their ACSII
-  values. Once the target string (character) is found in the key
-  array, its child pointer can be located through the same position in
-  the pointer array. Figure \ref{fig:character map} (a) shows a Map 4
+  values. Once the target character is found in the key array, its
+  child pointer can be located through the same position in the
+  pointer array. Figure \ref{fig:character map} (a) shows a Map 4
   structure with three keys: $f$, $n$ and $p$, where the triangles
@@
   through the array index which is the ASCII value of the target
-  character. Different from other sub-types of character maps, in Map
-  256, there is only one array and not necessary to carry out the
-  additional indirect access. Therefore, if most entries are not
-  empty, this representation is also very space efficient. Figure
+  character. Different from other character maps, in Map 256, there is
+  only one array, and it is not necessary to carry out the additional
+  indirect access. Therefore, if most entries are not empty, this
+  representation is also very space efficient. Figure
   \ref{fig:character map} (d) shows a Map 256 structure, where only
@@
     \STATE
-    \SWITCH{the sub-type of the character map}
+    \SWITCH{The type of the character map}
     \CASE{\textsf{Map 4}}
@@
 and the number of keys is not greater than 100 ($ndp \leq 100$), the
-\emph{string array} structure is constructed as a tree node. Similar
-to the Map 4 and Map 16 structures, the keys are stored in
+\emph{string array} structure is adopted as a tree node. Similar to
+the Map 4 and Map 16 structures, the keys are stored in
 lexicographical order in a separate key array of $ndp \times lss$
@@
 For efficiency, if the number of keys is less than 5, a naive linear
-search routine is used to search the target string in the key array;
+search is used to search the target string in the key array;
 otherwise, a more efficient (but complicated) binary search algorithm
@@
 heavy) data structure --- \emph{hash table} is adopted to deal with
-large number of keys. It is worth noting that, the procedure of
-building a hash table is directly based on the suffix set from which
-the prefix set is formed rather than the prefix set which is the basis
-of building other node structures. In this work, a hash table is an
-array of child pointers with each pointer initialized to $NULL$, and
-we also utilize a \emph{string hash function} which transforms a
+large number of keys. It is worth noting that, the construction of the
+hash table is directly based on the suffix set from which the prefix
+set is formed rather than the prefix set which is the basis of
+building other node structures. In our implementation, a hash table is
+an array of child pointers with each pointer initialized to $NULL$,
+and we also utilize a \emph{string hash function} which transforms a
 string to a positive integer.
@@
 hashed to an integer $i$ between 0 and $table\_size-1$ by the string
-hash function , then $suf$ is associated with the $i$-th slot of the
+hash function, then $suf$ is associated with the $i$-th slot of the
 hash table. After that, the suffixes whose length-$lss$ prefixes
@@
     \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
-    \STATE $new\_node \leftarrow$ adaptively create a tree node from
+    \STATE $new\_node \leftarrow$ Adaptively create a tree node from
     $SSF$, as shown in the \textbf{while} loop of Algorithm \ref{alg:amt}
@@
 is computed and used as the index of the hash table. If the
-corresponding slot is $NULL$, which means the target string fails to
-match any key in the hash table, the verification terminates and the
-engine moves to the next position; otherwise, the process goes to the
-tree node associated with that slot and compares the node with the
-corresponding substring in the text.
+corresponding slot is $NULL$, which means there is a mismatch, the
+verification terminates and the engine moves to the next position;
+otherwise, the process goes to the tree node associated with that slot
+and compares the node with the corresponding substring in the text.
 
@@
 by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
-uniform and universal. The form of the hash function family is shown
-in Algorithm \ref{alg:hash fun}.
+uniform and universal. The framework of the hash function family is
+shown in Algorithm \ref{alg:hash fun}.
 

### 2016-08-07 Engine.tex
添加: Dividng AMT

@@
 
-As mentioned before, our engine consists of the filter module and the
-verification module. In this section, we introduce the filter module,
-while in the next section the verification module will be illustrated.
+As mentioned before, our engine consists of a filter module and a
+verification module. In this section, we introduce the former, while
+in the next section the latter will be illustrated.
 
@@
 
-The filter we adopted in our engine is proposed by
-\cite{Lee2013}. Given the pattern set, as in the WM algorithm, only
-the length-$lsp$ prefix of each pattern are considering in
-constructing the filter, where $lsp$ is the \emph{length of the
-  shortest pattern} in the pattern set. Similar to WM, the filtering
-is based on character blocks (a character block is a short string
-consisting of only a few characters) rather than single
-characters. Given a block size $k$, the filter includes $lsp-k+1$
-membership query bitmaps denoted as $B_1$, $B_2$, \dots, and
-$B_{lsp-k+1}$, where each bitmap is a vector of $N$ bits. Let
-$B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be the
-$i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1 iff
-there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
+The filter we adopted in our engine is proposed by \cite{Lee2013},
+which is an improvement of the filter in the WM algorithm. Given the
+pattern set, as in the WM algorithm, only the length-$lsp$ prefix of
+each pattern are considering in constructing the filter, where $lsp$
+is the \emph{length of the shortest pattern} in the pattern
+set. Similar to WM, the filtering is based on character blocks (a
+character block is a merely short string consisting of only a few
+characters) rather than single characters. Given a block size $k$, the
+filter includes $lsp-k+1$ membership query bitmaps denoted as $B_1$,
+$B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap is a vector of $N$
+bits. Let $B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be
+the $i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1
+iff there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
 ($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
@@
 
+\subsection{Further Improvements}
+\label{sec:further improments}
+
+The verification module presented above is pretty efficient, but there
+are still some techniques that can further improve the time and space
+efficiency of this module.
+
+\subsubsection{Dividing the AMT}
+\label{sec:divide amt}
+
+The verification module we have just built is based on a big single
+AMT which is constructed from the whole pattern set. Actually, we can
+divide the big AMT into small ones and enable each verifying procedure
+to refer to only one small AMT, by which the time for verifying can be
+reduced. The division is based on the following observations.
+
+As stated in the filter module, for a position $i$ of the text $T$, if
+some pattern $p_j$ starts at $i$, there must be
+$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
+$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
+we can group the patterns according to their signatures: patterns with
+the same signature are grouped together to form a sub-pattern-set, and
+for each sub-pattern-set we build a (small) AMT from it. In addition,
+an index table is adopted to allow the corresponding AMT be retrieved
+in $O(1)$ time by its signature. Now, the verification module is made
+up of an index table and several small AMTs.
+
+Particularly, once a suspicious position $i$ in $T$ is detected, the
+value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
+find the corresponding small AMT for verifying $i$. As the scale of
+the AMT shr, the time for each verifying is reduced accordingly.
+
 \section{Experimental Results}

### 2016-08-08 Engine.tex
添加:node merge(未完成)

@@
 
-As stated in the filter module, for a position $i$ of the text $T$, if
-some pattern $p_j$ starts at $i$, there must be
-$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
+As stated in the filter module, the filtering is based on the last
+$k$-symbol block of the sliding window. In particular, for a position
+$i$ of the text $T$, if some pattern $p_j$ starts at $i$, there must
+be $Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
 $Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
@@
 the same signature are grouped together to form a sub-pattern-set, and
-for each sub-pattern-set we build a (small) AMT from it. In addition,
-an index table is adopted to allow the corresponding AMT be retrieved
-in $O(1)$ time by its signature. Now, the verification module is made
-up of an index table and several small AMTs.
+for each sub-pattern-set we build a (small) AMT. In addition, an index
+table is adopted to allow the corresponding AMT be retrieved in $O(1)$
+time by its signature. Now, the verification module is made up of an
+index table as well as several small AMTs.
 
@@
 find the corresponding small AMT for verifying $i$. As the scale of
-the AMT shr, the time for each verifying is reduced accordingly.
+the AMT shrunk, the time for each verifying is reduced accordingly.
+
+\subsubsection{Node Merge}
+\label{sec:node merge}
+
+The nodes in a path of AMT, each of which has only one key, can be
+merged into one node. This technique can reduce both time and space
+efficiency of the verification module. To illustrate this, consider
+the pattern set $P={p_1=, p_2=,p_3=}$ and its corresponding AMT
+constructed by the method presented in section . As shown in Fig , the
+built AMT has three nodes, and each of nodes has only one key. This
+AMT roughly takes bytes of memory ( bytes for the keys and 16 bytes
+for the child pointers), however, if we combine the three nodes into
+one, the keys will be merged into one string and the child pointers
+are no long needed. The only issue needs to be addressed is to
+distinguish the keys after they are merged.
 

### 2016-08-09 Engine.tex
继续撰写node merge部分(未完成)

@@
 
-As stated in the filter module, the filtering is based on the last
-$k$-symbol block of the sliding window. In particular, for a position
-$i$ of the text $T$, if some pattern $p_j$ starts at $i$, there must
-be $Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
+As stated in Section \ref{sec:filter}, the filtering is based on the
+last $k$-symbol block of the substring in the sliding window. In
+particular, for a position $i$ of the text $T$, if some pattern $p_j$
+starts at $i$, there must be
+$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
 $Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
@@
 
-Particularly, once a suspicious position $i$ in $T$ is detected, the
-value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
-find the corresponding small AMT for verifying $i$. As the scale of
-the AMT shrunk, the time for each verifying is reduced accordingly.
-
-\subsubsection{Node Merge}
+In the filtering phase, once a suspicious position $i$ in $T$ is
+detected, the value $Hash[T[i+lss-k,k]]$ will be used as the index of
+the index table to find the corresponding small AMT for verifying. As
+the scale of the AMT shrunk, the time for each verifying is reduced
+accordingly.
+
+\subsubsection{Node Merging}
 \label{sec:node merge}
@@
 efficiency of the verification module. To illustrate this, consider
-the pattern set $P={p_1=, p_2=,p_3=}$ and its corresponding AMT
-constructed by the method presented in section . As shown in Fig , the
-built AMT has three nodes, and each of nodes has only one key. This
-AMT roughly takes bytes of memory ( bytes for the keys and 16 bytes
-for the child pointers), however, if we combine the three nodes into
-one, the keys will be merged into one string and the child pointers
-are no long needed. The only issue needs to be addressed is to
-distinguish the keys after they are merged.
+the pattern set $P=\{p_1=e^6u^5sscc,\, p_2=e^6u^5,\, p_3=e^6\}$ and
+its corresponding AMT constructed by Algorithm 1. As shown in Fig (a),
+the built AMT has three nodes, and each contains only one key. In a
+typical x86\_64 architecture, this implementation of AMT roughly takes
+55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
+pointers and 24 bytes for the pointers to the matching
+functions. However, if we combine the three keys into one string, the
+three nodes can be merged into one node (Fig (b)), as a result, the
+child pointers are no longer needed and the number of function
+pointers is reduced from three to one. The merged node is another type
+of tree node in addition to the types we have introduced in Section
+\ref{subsec:nodes}.
+
+The only problem is to distinguish among the keys after they are
+concatenated, to address this issues, an \emph{length array} is used
+to store the length of each key, where each array element takes only
+one byte (using the \emph{unsigned char} type). From the length of
+each key, we can split the original keys out, and searching the target
+string in the merged node can be trivial.
+
+In general, after node merging, the AMT contains only one merged node
+which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
+array, and 8 bytes for the matching function pointer), thus, 29 bytes
+are saved comparing with the original AMT.
 

### 2016-08-10 Engine.tex
继续node merge部分(完成)

@@
 The verification module we have just built is based on a big single
-AMT which is constructed from the whole pattern set. Actually, we can
+AMT which is constructed from the whole pattern set. In fact, we can
 divide the big AMT into small ones and enable each verifying procedure
@@
 we can group the patterns according to their signatures: patterns with
-the same signature are grouped together to form a sub-pattern-set, and
-for each sub-pattern-set we build a (small) AMT. In addition, an index
+the same signature are grouped and form a sub-pattern-set, and for
+each sub-pattern-set we build a (small) AMT. In addition, an index
 table is adopted to allow the corresponding AMT be retrieved in $O(1)$
-time by its signature. Now, the verification module is made up of an
+time by its signature. Now, the verification module consists of an
 index table as well as several small AMTs.
@@
 
-The nodes in a path of AMT, each of which has only one key, can be
-merged into one node. This technique can reduce both time and space
-efficiency of the verification module. To illustrate this, consider
-the pattern set $P=\{p_1=e^6u^5sscc,\, p_2=e^6u^5,\, p_3=e^6\}$ and
-its corresponding AMT constructed by Algorithm 1. As shown in Fig (a),
-the built AMT has three nodes, and each contains only one key. In a
+Similar to the ``path compression'' technique widely used in trie-like
+structures, the nodes in a path of AMT, each of which has only one
+key, can be merged into one node. This technique can improve both time
+and space efficiency of AMT. To illustrate this, consider the pattern
+set $P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and its
+corresponding AMT constructed by Algorithm 1. As shown in Fig (a), the
+built AMT has three nodes, and each contains only one key. In a
 typical x86\_64 architecture, this implementation of AMT roughly takes
@@
 pointers and 24 bytes for the pointers to the matching
-functions. However, if we combine the three keys into one string, the
-three nodes can be merged into one node (Fig (b)), as a result, the
-child pointers are no longer needed and the number of function
+functions. However, if we combine the three keys into one string,
+these three nodes can be merged into one node (Fig (b)), as a result,
+the child pointers are no longer needed and the number of function
 pointers is reduced from three to one. The merged node is another type
@@
 
-The only problem is to distinguish among the keys after they are
-concatenated, to address this issues, an \emph{length array} is used
-to store the length of each key, where each array element takes only
-one byte (using the \emph{unsigned char} type). From the length of
-each key, we can split the original keys out, and searching the target
-string in the merged node can be trivial.
+For the merged node, the only problem is how to distinguish among the
+keys after they are concatenated, to address this issues, a
+\emph{length array} is used to store the length of each key, where
+each array element takes only one byte (using the \emph{unsigned char}
+type). Through the length of each key, we can split the original keys
+out, and searching the target string in the merged node can be
+trivial.
 
@@
 array, and 8 bytes for the matching function pointer), thus, 29 bytes
-are saved comparing with the original AMT.
+are saved comparing with the original AMT. In addition, only one
+random access to the memory is needed to get the merged node (the
+original AMT needs three random memory accesses to get all its nodes),
+thus, the cache can be fully used to improve the performance.
 

### 2016-08-12 Engine.tex
添加:node split 部分(未完成)

@@
 
-Similar to the ``path compression'' technique widely used in trie-like
-structures, the nodes in a path of AMT, each of which has only one
-key, can be merged into one node. This technique can improve both time
-and space efficiency of AMT. To illustrate this, consider the pattern
-set $P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and its
-corresponding AMT constructed by Algorithm 1. As shown in Fig (a), the
-built AMT has three nodes, and each contains only one key. In a
-typical x86\_64 architecture, this implementation of AMT roughly takes
-55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
-pointers and 24 bytes for the pointers to the matching
+Similar to the ``path compression'' technique that is widely used in
+many trie-like structures, the nodes in a path of AMT, each of which
+has only one key, can be merged into one node. This technique can
+improve both time and space efficiency of AMT. To illustrate its
+benefits, consider the pattern set
+$P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and the corresponding
+AMT constructed by Algorithm 1. As shown in Fig (a), the built AMT has
+three nodes, and each contains only one key. In a typical x86\_64
+architecture, this implementation of AMT roughly takes 55 bytes of
+memory: 15 bytes for the three keys, 16 bytes for the two child
+pointers and 24 bytes for the three pointers to the matching
 functions. However, if we combine the three keys into one string,
@@
 pointers is reduced from three to one. The merged node is another type
-of tree node in addition to the types we have introduced in Section
-\ref{subsec:nodes}.
+of tree node in addition to the node types we have introduced in
+Section \ref{subsec:nodes}.
 
@@
 each array element takes only one byte (using the \emph{unsigned char}
-type). Through the length of each key, we can split the original keys
-out, and searching the target string in the merged node can be
+type). Through the length of each key, we can delimit each original
+keys, and thus, searching the target string in the merged node can be
 trivial.
 
-In general, after node merging, the AMT contains only one merged node
-which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
-array, and 8 bytes for the matching function pointer), thus, 29 bytes
-are saved comparing with the original AMT. In addition, only one
+In general, after node merging, the AMT contains just one merged node
+which only takes 26 bytes (15 bytes for the keys, 3 bytes for the
+length array, and 8 bytes for the matching function pointer), thus, 29
+bytes are saved comparing with the original AMT. In addition, only one
 random access to the memory is needed to get the merged node (the
 original AMT needs three random memory accesses to get all its nodes),
-thus, the cache can be fully used to improve the performance.
+thus, the cache miss is reduced and the performance is improved.
+
+\subsubsection{Node splitting}
+\label{sec:node split}
+
+Once the keys in a node share a common prefix, that prefix can be
+removed from the keys and form a new single key node (since the prefix
+is either a character or a string, the type of the new node is either
+Map 4 or String Array). This technique can reduce a lot of redundant
+comparisons while searching a target key in that node. For instance,
+consider the node in Fig whose four keys share a common prefix $a^4$,
+and a target key which is $a^4u$. it will be compared with the four
+keys in order and finally takes $5 \times 4 = 20$ byte comparisons to
+determine the inexistence of target key. However, if $a^4$ is split
+out and form another new node as shown in Fig , for the same target,
+only 8 byte comparisons (4 comparisons for $node_1$ and another 4
+comparisons for $node_2$) is needed.
 

### 2016-08-21 Engine.tex
继续撰写node split部分,本次提交为了测试ssh

@@
 Once the keys in a node share a common prefix, that prefix can be
-removed from the keys and form a new single key node (since the prefix
-is either a character or a string, the type of the new node is either
-Map 4 or String Array). This technique can reduce a lot of redundant
-comparisons while searching a target key in that node. For instance,
-consider the node in Fig whose four keys share a common prefix $a^4$,
-and a target key which is $a^4u$. it will be compared with the four
-keys in order and finally takes $5 \times 4 = 20$ byte comparisons to
-determine the inexistence of target key. However, if $a^4$ is split
-out and form another new node as shown in Fig , for the same target,
-only 8 byte comparisons (4 comparisons for $node_1$ and another 4
-comparisons for $node_2$) is needed.
+removed from the keys and form a new single key node. This technique
+can reduce a lot of redundant comparisons while searching a target key
+in a node. For instance, consider searching a target key $a^5u$ in a
+string array type node whose four keys share a common prefix $a^5$, as
+shown in Fig . According to Algorithm \ref{alg:string array}, the
+target key have to be compared sequentially with the four keys in the
+node, which will totally takes $6 \times 4 = 24$ byte comparisons to
+determine the inexistence of target key. However, if the common prefix
+$a^5$ is split out and form another new node as shown in Fig , for the
+same target, only 9 byte comparisons (5 comparisons for $node_1$ and
+another 4 comparisons for $node_2$) are needed for
+searching. Comparing with only one node, the two nodes can reduce 15
+comparisons. Note that, since the prefix is either a character or a
+string, the new node is either a Map 4 node or a String Array node.
 

### 2016-08-22 Engine.tex
完善node spliting

@@
 
-due to the effectiveness of the filter and the compactness of the AMT
-whether there are patterns starting at that position
+% due to the effectiveness of the filter and the compactness of the AMT
+% whether there are patterns starting at that position
 
@@
 
-Once the keys in a node share a common prefix, that prefix can be
-removed from the keys and form a new single key node. This technique
+In order to further improve the searching efficiency of tree nodes,
+once the keys in a node share a common prefix, that prefix should best
+be removed from the keys and form a new single key node. This method
 can reduce a lot of redundant comparisons while searching a target key
 in a node. For instance, consider searching a target key $a^5u$ in a
-string array type node whose four keys share a common prefix $a^5$, as
-shown in Fig . According to Algorithm \ref{alg:string array}, the
+node of string array type, whose four keys share a common prefix $a^5$
+, as shown in Fig . According to Algorithm \ref{alg:string array}, the
 target key have to be compared sequentially with the four keys in the
@@
 determine the inexistence of target key. However, if the common prefix
-$a^5$ is split out and form another new node as shown in Fig , for the
-same target, only 9 byte comparisons (5 comparisons for $node_1$ and
-another 4 comparisons for $node_2$) are needed for
-searching. Comparing with only one node, the two nodes can reduce 15
-comparisons. Note that, since the prefix is either a character or a
-string, the new node is either a Map 4 node or a String Array node.
+$a^5$ is removed out of the keys and form another new node as shown in
+Fig , for the same target, only 9 byte comparisons are needed for
+verifying (5 comparisons for $node_1$ and another 4 comparisons for
+$node_2$). Note that, since the prefix is either a character or a
+string, the type of the new node is either Map 4 or String
+Array. Obviously, comparing with only one node, the two nodes version
+can reduce 15 comparisons, which .
 

### 2017-02-04 response.tex
revised

\documentclass{paper}

\title{Author's response to the review of No.IJPRAI-D-16-00429}

\begin{document}

\begin{center}
{\Large \textbf{Author's response to the review of No.IJPRAI-D-16-00429\\[20pt]}}
\end{center}

\textbf{Dear Editors and Reviewers:\\}

We would like to thank the reviewers and associate editors for their
valuable and constructive comments and suggestions. Based on these
comments and suggestions, we revised the paper, and the main revisions
are as follows.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 1}\\
\end{center}

\textbf{1.} The construction of AMT used a breadth-first search
strategy, why does not use a depth-first strategy instead? Is there
some inherent reasons? Please give an explanation.\\[7pt]
\noindent \textbf{Response:} There is no essential distinction between
the breadth-first strategy and the depth-first strategy in
constructing the AMT. If the breadth-first strategy is adopted, the
AMT will be built level by level; on the other hand, if the
depth-first strategy is used, the AMT will be built branch by
branch. But regardless of the strategies used, the final built AMTs
are the same. We choose the breadth-first strategy to build the AMT
level by level, and we have added this explanation to Section 5.1.\\

\textbf{2.} Is the hash function used in the "Hash Table" node
structure the same as in other algorithms such as WM and
Pre-filter+AC?\\[7pt]
\noindent \textbf{Response:} No, they are not the same. The hash
functions used by the WM and Pre-filter+AC algorithms apply
essentially to short strings which consist no more than 3 characters,
whereas the hash function used in the \emph{hash node} must be able to
process longer strings with more than 3 characters. Therefore, we
choose the \emph{shift-add-xor} hash family for the hash node to
process long
strings.\\

\textbf{3.} The chosen of the parameters is very important for
building the tree nodes. Please give a more detailed instruction to
the chosen of the parameters in section 6.1.\\[7pt]
\noindent \textbf{Response:} For String Arrays containing no more than
\textbf{4} strings, the simple linear search is faster than binary
search due to the complexity of binary search. The load factor of the
Hash Table is set to \textbf{0.5}, which is a good balance between
time and space. The parameters about the hash function are chosen from
its original paper, which are claimed to be very efficient. We have
tested that once $ndp > 100$, the hash table structure becomes more
efficient than the String Array structure. All these detailed
explanations for parameter
selections have been added to section 6.1.\\

\textbf{4.} The captions and some table items in table 2, 3 and 4 are
not very clear, please revise them.\\[7pt]
\noindent \textbf{Response:} The captions of Table 2, 3 and 4 are
revised. The \emph{Sing Char} and \emph{Single String} items in these
tables are modified to \emph{Map 1} and \emph{Single String Array}, respectively.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 2}\\
\end{center}

\textbf{1.} Is the hash function used in the \emph{Hash Table} node structure
the same as in the filter module?\\[7pt]
\noindent \textbf{Response:} No, they are not the same. The hash
function used in the \emph{Hash Table} node comes from the
\emph{shift-add-xor} hash family which is able to process long
strings, whereas the hash function used in the filter module is
usually a direct map which maps a short string to its decimal
representation.\\

\textbf{2.} Please explain how the two parameters $N$ and $k$ are chosen in the
filter module.\\[7pt]
\noindent \textbf{Response:} If $lsp \leq 5$, set $k = 2$; otherwise,
set $k=3$. $N$ is set to be $|\Sigma|^k$. We have added this comments
to Section 4.\\

\textbf{3.} The authors choose to use a breadth-first strategy to
build the AMT, is it possible to use a depth-first strategy instead?
\noindent \textbf{Response:} Absolutely yes. Regardless of which
strategies are used, the final constructed AMTs are the same.

\textbf{4.} The example (Fig.2) in the filter module does not clearly
show the interaction with the verification module. Please add some
detailed illustrations.
\noindent \textbf{Response:} Every time the filter module detects a
potential matched position in the text (i.e., the last bit of
$MB~\&~QB$ is 1), the verification module is invoked to check if there
exists patterns starting at that position, and in the mean while, the
matching window stops at that position, once the verification
finishes, the filter module moves the matching window to the next
position. We have added this detailed procedure to Section 4.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 3}
\end{center}

There is no comments from reviewer 3.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 4}
\end{center}

\textbf{1.} The novelty or fresh new ideas is not very clear, does not
have enough comparisons with other methods in the literature.\\[7pt]
\noindent \textbf{Response:} The major contributions of this paper
are: 1. A novel data structure called Adaptive Matching Tree (AMT) is
proposed to store the string pattern set efficiently. 2. A fast engine
based on AMT is proposed, which is able to process large-scale string
pattern sets. In addition, we have added another comparison with
a recent algorithm to the experiment part of our paper.\\

\textbf{2.} What is its relation to PR \& AI ? (Pattern Recognition \&
Artificial Intelligence) Should explain it more clearly.\\[7pt]
\noindent \textbf{Response:} The term \emph{pattern} has various
meanings in various fields. In this paper, the term \emph{pattern} is
specified to \emph{string pattern}, and accordingly \emph{pattern
  recognition} is specified to \emph{string pattern searching}, which
is one of the
oldest and fundamental problems in computer science.\\

\textbf{3.} Need to add more recent related publications in the
reference list including , for examples 2015, 2016 PR \& AI subfield.\\[7pt]
\noindent \textbf{Response:} We have already added several recent
published (in 2015 or 2016) references
about PR \& AI to our paper.\\

\textbf{4.} Compare your work with others in the literature,
advantages vs disadvantages, in depth and width.\\[7pt]
\noindent \textbf{Response:} We have added another comparison in our
experiment to a recent published multi-string pattern matching
algorithm called \textsf{Split} proposed by \emph{Kim, HyunJin AND
  Choi, Kang-Il AND Choi, Sang-Il. A Memory-Efficient Deterministic
  Finite Automaton-Based Bit-Split String Matching Scheme Using
  Pattern Uniqueness in Deep Packet
  Inspection. PLOS ONE. vol.10. pp.1-24. 2015.}\\

\textbf{5.} Should use real images with noisy and testing samples set
size should be large enough to show your results are indeed
convincing,
reliable, and meaningful.\\[7pt]
\noindent \textbf{Response:} Unfortunately, our method only focuses
on string patterns, so it does not apply to images.\\

\textbf{6.} This paper is not very well written. Its English
presentation is not good enough. Should consult English technical
writing expert to help.\\[7pt]
\noindent \textbf{Response:} We have carefully revised the paper again
to improve its presentation, so we hope it is more readable and easy
to understand now.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2017-02-04 A_Fast_Engine_for_Multi_string_Pattern_Matching(revised).tex
revised

--- 2016-08-12 Engine.tex
@@
-\documentclass{article}
-
-\usepackage[numbers]{natbib}
-\citestyle{IEEEtran}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Trim Size: 9.75in x 6.5in
+%% Text Area: 8in (include Runningheads) x 5in
+%% ws-ijprai.cls   :   8-8-2014
+%% Class file to use with ws-ijprai.tex written in Latex2E.
+%% The content, structure, format and layout of this style file is the
+%% property of World Scientific Publishing Co. Pte. Ltd.
+%% Copyright 2014 by World Scientific Publishing Co.
+%% All rights are reserved.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+
+\documentclass{ws-ijprai}
+\usepackage{enumerate}
 
@@
 \usepackage{color}
+\usepackage{pgfplots}
+
 \newcommand{\SWITCH}[1]{\STATE \textbf{switch} (#1)}
@@
 
-% \title{An Efficient Adaptive Architecture for Muliti-pattern Matching}
-% \author{Zhan Peng  Yuping Wang}
- %\maketitle
-
 \begin{document}
 
-\bibliographystyle{alpha}
-
-\begin{center}
-{\Large An Fast Engine for Large-scale String Pattern Matching}
-\end{center}
+\markboth{Zhan Peng et al.}{A Fast Engine for Multi-string Pattern Matching}
+
+%%%%%%%%%%%%%%%%%%%%% Publisher's area please ignore %%%%%%%%%%%%%%%
+%
+\catchline{}{}{}{}{}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{A Fast Engine for Multi-string Pattern Matching}
+
+\author{Zhan Peng, Yuping Wang\footnote{Corresponding author}~, Wei Yue}
+
+\address{$^1$School of Computer Science and Technology\\
+  Xidian University\\
+  Xi'an, Shaanxi, 710071, China\\
+   $^*$ywang@xidian.edu.cn
+}
+
+\maketitle
+
+%begin{history}
+%received{(Day Month Year)}
+%revised{(Day Month Year)}
+%accepted{(Day Month Year)}
+%comby{(xxxxxxxxxx)}
+%end{history}
 
 \begin{abstract}
-  Multi-string matching is the core technique that is widely used in
-  many applications. In general, it searches a text string for all
-  occurrences of some string patterns. However, as the number of
-  string patterns increases, most of the existing algorithms suffer
-  from two issues: the long matching time, and the high memory
-  consumption. To address these issues, in this paper, a fast matching
-  engine is proposed for large-scale string matching problems. Our
-  engine includes a filter module and a verification module. The filter
-  module is based on several bitmaps, which is response for quickly
-  filtering out the invalid positions in the text, while for each
-  potential matched position, the verification module confirms true
-  pattern occurrence. In particular, we design a compact data
-  structure called Adaptive Matching Tree (AMT) as the verification
-  module, in which each tree node saves some pattern fragments of the
-  whole pattern set. The key point is that, the inner structure of
-  each tree node is chosen adaptively according to the features of the
-  corresponding pattern fragments, and this makes the whole AMT both
-  time and space efficient for verifying. The experiments indicate
-  that, our matching engine performs better than the prior algorithms,
-  especially for large pattern sets.
+  Multi-string matching is a core technique searching a text string
+  for all occurrences of some string patterns. It is widely used in
+  many applications. However, as the number of string patterns
+  increases, most of the existing algorithms suffer from two issues:
+  the long matching time, and the high memory consumption. To address
+  these issues, in this paper, a fast matching engine is proposed for
+  large-scale string matching problems. Our engine includes a filter
+  module and a verification module. The filter module is based on
+  several bitmaps which are response for quickly filtering out the
+  invalid positions in the text, while for each potential matched
+  position, the verification module confirms true pattern
+  occurrence. In particular, we design a compact data structure called
+  Adaptive Matching Tree (AMT) for the verification module, in which
+  each tree node only saves some pattern fragments of the whole
+  pattern set and the inner structure of each tree node is chosen
+  adaptively according to the features of the corresponding pattern
+  fragments. This makes the engine time and space efficient. The
+  experiments indicate that, our matching engine performs better than
+  the compared algorithms, especially for large pattern sets.
 \end{abstract}
 
-{\textbf{Key words}: String Matching; Pattern Matching; Dictionary Matching}
-
-due to the effectiveness of the filter and the compactness of the AMT
-whether there are patterns starting at that position
+\keywords{String Matching; Pattern Matching; Dictionary Matching}
+
+% due to the effectiveness of the filter and the compactness of the AMT
+% whether there are patterns starting at that position
 
@@
 The MSM is a primitive but critical operation used in many
-applications such as information retrieval, intrusion detection
-system, information extraction, text editing, etc. In general, it
-seeks all positions in a text string that match any of the string
-patterns in a given pattern set. Efficient algorithms for MSM scan the
-text only once, searching for all patterns
-concurrently. Traditionally, these algorithms include two major
-phases, i.e. the \textsf{preprocessing phase} and the \textsf{matching
-  phase}. In the \textsf{preprocessing phase}, a suitable data
-structure is constructed to store all the string patterns, and then
-the \textsf{matching phase} scans and compares the given text with the
-data structure for finding all occurrences every pattern in the
-text. It is obvious that the time and space efficiency of the data
-structure built in the preprocessing phase can have a significant
-impact on the performance of the algorithm in the matching phase.
-
-% Preferably, an algorithm scans the text once so that its performance
-% should mainly depend on the size of the text rather than the features
-% of pattern sets. However, the performance of lots of existing
-% algorithms for MSM is affected seriously by the pattern sets. For
-% instance, many algorithms, such as the classical \textsf{Wu-Manber}
-% (\textsf{WM}) algorithm or the more recent \textsf{Pre-filter+AC}
-% scheme, can not efficiently deal with the pattern sets containing very
-% short patterns. When encountering such pattern sets, the performance
-% of these algorithm degrades dramatically. This is due to the internal
-% design of the data structure which is used for
-% matching. {\color{red}{Therefore, it's quite valuable to design a data
-% structure that can efficiently support pattern sets with various
-% features. Using this kind of data structure can improve the robustness
-% of MSM.}}
-
-In the big data context nowadays the number of patterns to be matched
-becomes huge in some applications, for instance, the database of a
-modern anti-virus/intrusion-detection system can easily contain
-millions, or even tens of millions number of virus
-signatures/rules. However, the existing algorithms are not suitable
-for such applications with very large pattern sets. Because on the one
-hand, the throughout of these methods can not keep up with the demand
-of the applications as the number of patterns increases, which is due
-to the poor scalability of the data structures used by these methods,
-and on the other hand, the data structure of several algorithms (such
-as the \textsf{AC} algorithm) is not space efficient, which means they
-can not process large pattern sets with limited memory. Therefore it
-is very valuable to design space-efficient data structures with good
-scalability to support applications requiring large-scale string
-matching.
-
-In this paper, we propose a multi-string matching engine for large
-string pattern sets. Similarly to the traditional approaches, our
-strategy consists of the preprocessing phase and the matching
-phase. In the preprocessing phase, the matching engine is constructed
-based on the pattern set. Then in the matching phase, the engine takes
-the text string as input, and searches the occurrences of each
-pattern in the text.
+applications such as pattern recognition \cite{Yan2016},
+\cite{Xiao2016}, ontology alignments \cite{Xue2015} \cite{Xue2016},
+text classification \cite{Tang2015} \cite{Zhang2016}, intrusion detection system
+\cite{Kim2015}, etc. In general, it seeks all positions in a text
+string that match any of the string patterns in a given pattern
+set. An efficient algorithm for MSM only needs to scan the text once
+and finds all patterns concurrently. Traditionally, the existing
+algorithms include two major phases, i.e. the \textsf{preprocessing
+phase} and the \textsf{matching phase}. In the \textsf{preprocessing
+phase}, a suitable data structure is constructed to store all the
+string patterns, and then the \textsf{matching phase} scans and
+compares the given text with the data structure to find all
+occurrences of every pattern in the text. It is obvious that the time
+and space efficiency of the data structure built in the preprocessing
+phase can have a significant impact on the performance of the
+algorithm in the matching phase.
+
+Nowadays, the number of patterns to be matched becomes huge in some
+applications, for instance, the database of a modern
+anti-virus/intrusion-detection system can easily contain millions
+number of virus signatures/rules. However, the existing algorithms are
+not suitable for such applications with very large pattern sets due to
+two main reasons: 1) The poor scalability of the data structures used;
+2) The space inefficiency of the data structure used, which means
+these algorithms can not process large pattern sets with limited
+memory. Moreover, the existing algorithms are sensitive to the length
+of the patterns, particularly the length of the shortest pattern. Many
+algorithms can not efficiently deal with pattern set containing very
+short pattern due to the poor robustness of their data
+structures. Therefore, it is very valuable to design space-efficient
+data structures with good scalability and robustness to support
+applications requiring large-scale string matching.
+
+In this paper, we propose a multi-string matching engine with good
+robustness for large string pattern sets. Similarly to the existing
+efficient approaches, our approach consists of the preprocessing phase
+and the matching phase. In the preprocessing phase, the matching
+engine is constructed based on the pattern set. Then in the matching
+phase, the engine takes the text string as input, and searches the
+occurrences of each pattern in the text.
 
 The proposed engine consists of a filter module and a verification
-module. The function of the filter module is to find the potential matched
-positions in the text. Once such a position is found, the verification
-module confirms whether there are patterns starting at that
-position. The filter we adopted is proposed by \cite{Lee2013}, which
-is based on several bitmaps and a group of simple bitwised \emph{and}
-and \emph{shift} operations. In the matching phase, the engine queries
-the bitmaps to check the validity of the current position: if the
-current position is a potential matched position, the verification
-unit is invoked; otherwise, the engine skips over this position (as
-well as the next few positions if possible). In particular, the
-authors proved that the proposed filter is optimal in the sense that
-it is able to utilizing all previous query results, which means the
-filter can skip as many invalid positions as possible. For the
-verification module, we design a compact tree-like data structure called
-Adaptive Matching Tree (\textsf{AMT}) based on the pattern
-set. Specifically, the whole pattern set is gradually partitioned into
-several small parts first, and then the pattern fragments of each
-small part is stored in a separate node of the AMT for subsequent
-matching. The key point is that, the inner structure of each tree node
-is selected adaptively according to the features of the pattern
-fragments, and this adaptivity guarantees a high matching speed as
-well as a low memory consumption for each tree node, as a result, the
-whole AMT would be both time and space efficient for verifying in the
-matching phase.
+module. The function of the filter module is to find the potential
+matched positions in the text. Once such a position is found, the
+verification module confirms whether there are patterns starting at
+that position. The filter adopted is proposed in \cite{Lee2013}, which
+is based on several bitmaps and a group of simple bit-wised
+"\emph{and}" and "\emph{shift}" operations. In the matching phase, the
+engine queries the bitmaps to check the validity of the current
+position: if the current position is a potential matched position, the
+verification module is invoked; otherwise, the engine skips over this
+position as well as the next few positions as many as possible. In
+fact, the filter is proved to be optimal in the sense that it is able
+to utilizing all previous query results, and thus can skip as many
+invalid positions as possible. For the verification module, we design
+a compact tree-like data structure called Adaptive Matching Tree
+(\textsf{AMT}) based on the pattern set. Specifically, the whole
+pattern set is gradually partitioned into several small parts first,
+and then the pattern fragments of each small part is stored in a
+separate node of the AMT for subsequent matching. The critical feature
+of AMT is that, the inner structure of each tree node is changed
+adaptively according to the features of the pattern fragments, and
+this adaptivity guarantees a high matching speed as well as a low
+memory consumption for each tree node, as a result, the whole AMT
+would be both time and space efficient for verifying in the matching
+phase.
 
@@
 \ref{sec:notations} lists the notations and terminology used in this
-paper. Section \ref{sec:ADSM} describes our matching engine in
-details. Section \ref{sec:experiments} presents the performance
-evaluations. Section \ref{sec:conclusion} concludes the paper and
-proposes some open problems.
+paper. Section \ref{sec:filter} describes the filter module. Section
+\ref{sec:verification} presents the verification module. Section
+\ref{sec:experiments} presents the performance evaluations. Section
+\ref{sec:conclusion} concludes the paper and proposes some open
+problems.
 
@@
 not suitable for MPM. The \textsf{AC} algorithm is a generalization of
-the \textsf{KMP} algorithm, by preprocessing the patterns and building
+the \textsf{KMP} algorithm by preprocessing the patterns and building
 a deterministic finite automaton (DFA) that can match multiple
@@
 
-To reduce the memory requirement of \textsf{AC}, Tuck[2004] proposed a
-algorithm called \textsf{Bitmapped AC}. This algorithm uses the bitmap
-data structure to replace the conventional child pointers in each
-state. In addition, it uses a path compression technique which can
-merge successive single-child states into one state. It is reported
-that, the compression optimization of \textsf{Bitmapped AC} results in
-a 50 times reduction in memory consumption over the default
-\textsf{AC} algorithm. However, since traversal from node to node
-requires checking a bit in a bitmap and then performing a sum up to
-256 prior bits in the bitmap, the average performance of this
-algorithm is not high.  Another algorithm to reduce the space
-requirement is the \textsf{Compressed AC} algorithm proposed by
-Bremeler-Barr[2011]. In addition to use a similar path compression
-method, this algorithm also develops a technique that can eliminate
-the leaf states. The experiment shows that \textsf{Compressed AC} can
-reduce at most $60\%$ memory requirement compared with the
-traditionally \textsf{AC} algorithm. But the similar problem is, it
-only works well for a few pattern sets.  Lee[2013] proposed an
-algorithm called \textsf{Pre-filter+AC}. As the name shows, this
-algorithm consists of a pre-filter and a verification engine. The
-function of the pre-filter is to query data structures built from
-patterns to find the starting positions of potential pattern
-occurrences. Once a suspicious starting position is found, the
+To reduce the memory requirement of \textsf{AC}, Tuck \cite{Tuck2004}
+proposed an algorithm called \textsf{Bitmapped AC}. This algorithm
+uses the bitmap data structure to replace the conventional child
+pointers in each state. In addition, it uses a path compression
+technique which can merge successive single-child states into one
+state. It is reported that, the compression optimization of
+\textsf{Bitmapped AC} results in a 50 times reduction in memory
+consumption over the default \textsf{AC} algorithm. However, since
+traversal from node to node requires checking a bit in a bitmap and
+then performing a sum up to 256 prior bits in the bitmap, the average
+performance of this algorithm is not high.  Another algorithm to
+reduce the space requirement is the \textsf{Compressed AC} algorithm
+proposed by \cite{Bremler2011}. In addition to use a similar path
+compression method, this algorithm also develops a technique that can
+eliminate the leaf states. The experiment shows that
+\textsf{Compressed AC} can reduce at most $60\%$ memory requirement
+compared with the traditionally \textsf{AC} algorithm. But it only
+works well for problems with a few pattern sets. Lee \cite{Lee2013}
+proposed an algorithm called \textsf{Pre-filter+AC}. As the name
+shows, this algorithm consists of a pre-filter and a verification
+engine. The function of the pre-filter is to query data structures
+built from patterns to find the starting positions of potential
+pattern occurrences. Once a suspicious starting position is found, the
 verification engine confirms true pattern occurrence. The pre-filter
@@
 candidate patterns simultaneously rather than sequentially. However,
-as the author stated, the pre-filter is suitable for patterns of
+as the author mentioned, the pre-filter is suitable for patterns of
 moderate or large lengths. For short patterns, its throughput
-degrades.
+degrades. Recently, Kim \cite{Kim2015} proposed a memory-efficient
+algorithm \textsf{Split} for deep packet inspection system, which
+consists of multiple finite-state machine.
 
@@
 $20\%$ in average, moreover, when $lsp < 5$ the \textsf{$L^{+1}$-MWM}
-gains an $38.87\%$ enhancement.
+gains a $38.87\%$ enhancement.
 
@@
 set. The compressed pattern set are then transformed to a pipelined
-binary tree tree which will be used in the matching phase. It is
-reported that, the \textsf{MASM} achieves a memory efficiency (defined
-as the ratio of the amount of the required storage in bytes and the
-size of the pattern set in number of characters) of 0.56 for the
-Rogets dictionary and 1.32 for the Snort rule set. Moraru
-\cite{Moraru2012} also presented a memory-efficient and
-cache-optimized algorithm for large pattern sets. This algorithm
-builds upon the Rabin-Karp \cite{Karp1987} SPM algorithm and
-incorporates a new \textsf{feed-forward} bloom filter which takes into
-account the memory hierarchy of modern computers. This algorithm is
-also well suited for implementation on GPUs which enables the matching
-to be done in parallel.
+binary tree which will be used in the matching phase.  It is reported
+that, the \textsf{MASM} achieves a memory efficiency (defined as the
+ratio of the amount of the required storage in bytes and the size of
+the pattern set in number of characters) of 0.56 for the Rogets
+dictionary and 1.32 for the Snort rule set. Moraru \cite{Moraru2013}
+also presented a memory-efficient and cache-optimized algorithm for
+large pattern sets. This algorithm builds upon the Rabin-Karp
+\cite{Karp1987} SPM algorithm and incorporates a new
+\textsf{feed-forward} bloom filter which takes into account the memory
+hierarchy of modern computers. This algorithm is also well suited for
+implementation on GPUs which enables the matching to be done in
+parallel.
 
@@
   lists} data structure to allow the pattern set to be updated
-dynamically in a optimal time. Amir \cite{Amir2015} introduced an
+dynamically in an optimal time. Amir \cite{Amir2015} introduced an
 algorithm for the gapped MPM problem, where each pattern in the
@@
 \textsf{suffix} of $S$ that starts at position $m+1$, is the substring
-left after removing the length-$m$ prefix of $S$. It is
-denoted by $S^{-m}$, i.e. $S^{-m} = S[m+1,\,|S|-m]$.\\
+left after removing the length-$m$ prefix of $S$. It is denoted by
+$S^{-m}$, i.e. $S^{-m} = S[m+1,\,|S|-m]$. (Particularly, a string $S$
+can be regarded as a prefix/suffix of itself, i.e. $S=S^{+|S|}=S^{-0}$.)\\
 \\
-Actually, a string $S$ can be regarded as a prefix/suffix of itself,
-i.e. $S=S^{+|S|}=S^{-0}$. Finally, the MSM problem can be
-formally defined as follows: \\
+Finally, the MSM problem can be defined as follows: \\
 \\
@@
 $(1 \leq i \leq k)$ are all strings over $\Sigma$. The multi-string
-pattern matching is to find all occurrences of every pattern of $P$ in
+matching problem is to find all occurrences of every pattern of $P$ in
 $T$, more formally, to build the result set
@@
 
-% the whole pattern set is transformed to a compact tree-like structure
-% called Adaptive Matching Tree (AMT), where each tree node is built
-% adaptively to save the information of a small part of the pattern
-% set. While in the matching phase, the built AMT is compared against
-% the text string to search patterns in that string. The framework of
-% constructing the AMT from the pattern set is introduced in Section
-% \ref{subsec:amt}, and using the AMT to search patterns in the text
-% string is described in Section \ref{subsec:matching}, finally
-% adaptively creating the tree nodes is presented in Section
-% \ref{subsec:nodes}.
-
 The filter we adopted in our engine is proposed by \cite{Lee2013},
@@
 pattern set, as in the WM algorithm, only the length-$lsp$ prefix of
-each pattern are considering in constructing the filter, where $lsp$
-is the \emph{length of the shortest pattern} in the pattern
-set. Similar to WM, the filtering is based on character blocks (a
-character block is a merely short string consisting of only a few
-characters) rather than single characters. Given a block size $k$, the
-filter includes $lsp-k+1$ membership query bitmaps denoted as $B_1$,
-$B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap is a vector of $N$
-bits. Let $B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be
-the $i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1
-iff there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
-($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
-where $hash$ is a hash function that maps a $k$-symbol block to an
-integer in the range of $[0, N-1]$.
-
-Fig shows an example, assume that alphabet
-$\Sigma = \{0, 1, 2, \dots, 9\}$ and pattern set
+each pattern are considered in constructing the filter, where $lsp$ is
+the \emph{length of the shortest pattern} in the pattern set. Similar
+to WM, the filtering is based on character blocks (a character block
+is merely a short string consisting of only a few characters) rather
+than single character. Assuming that each block consists of $k$
+characters, the filter will include $lsp-k+1$ membership query bitmaps
+denoted as $B_1$, $B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap
+is a vector of $N$ bits. (If $lsp \leq 5$, set $k = 2$; otherwise, set
+$k=3$. $N$ is set to be $|\Sigma|^k$). Let $B_j[i]$,
+$0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be the $i$-th bit of
+the $j$-th query bitmap, and $B_j[i]$ is set to 1 iff there exists a
+pattern $p_m$ such that $hash(p_m[j,k]) = i$ ($p_m[j,k]$ is a
+$k$-symbol block starting at position $j$ of $p_m$), where $hash$ is a
+hash function that maps a $k$-symbol block to an integer in the range
+of $[0, N-1]$.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=2in, width=2in]{./eps/filter}
+  \caption{The filter constructed from three digital patterns.}
+  \label{fig:filter}
+\end{figure}
+
+Figure \ref{fig:filter} shows an example of the filter, assume that
+alphabet $\Sigma = \{0, 1, 2, \dots, 9\}$ and pattern set
 $P = \{p_1,\; p_2,\; p_3\}$, where $p_1 = 04648753$, $p_2 = 30692$,
-and $p_3 = 614621$. Obviously, there is $lsp = |p_2|= 5$. Assume that
-$k = 2$, $N = 100$, and the hash function is the identity mapping. For
-such a setting, there are $lsp - k + 1 = 4$ query bitmaps, i.e. $B_1$,
-$B_2$, $B_3$, $B_4$, and in particular, we have $B_1[i] = 1$ iff $i$ =
-4, 30, or 61; $B_2[i] = 1$ iff $i$ = 6, 14, or 46; $B_3[i] = 1$ iff
-$i$ = 46, 64, or 69; and $B_4[i] = 1$ iff $i$ = 48, 62, or 92.
-
-% In addition, another bitmap of $lsp-k+1$ bits, which is called
-% \emph{master bitmap} and denoted by
-% $MB = mb_1mb_2 \dots mb_{lsp-k+1}$, is adopted to accumulate the
-% previous query results and act as the current state of the filter.
+and $p_3 = 614621$.  Obviously, $lsp = |p_2|= 5$. Assume that $k = 2$,
+$N = 100$, and the hash function is the identity mapping. For such a
+setting, there are $lsp - k + 1 = 4$ query bitmaps, i.e. $B_1$, $B_2$,
+$B_3$, $B_4$, and in particular, we have $B_1[i] = 1$ iff $i$ = 4, 30,
+or 61; $B_2[i] = 1$ iff $i$ = 6, 14, or 46; $B_3[i] = 1$ iff $i$ = 46,
+64, or 69; and $B_4[i] = 1$ iff $i$ = 48, 62, or 92.
 
@@
 the text string $T$. Initially, $W$ is aligned with the beginning of
-$T$, so that the substring of $T$ contained in $W$ is $T[1,lsp]$. In
-general, assume that $W$ is moved to the $i$-th position of $T$, and
+$T$, so that the substring of $T$ contained in $W$ is $T[1,lsp]$.
+Generally, assume that $W$ is moved to the $i$-th position of $T$, and
 the substring of $T$ contained in $W$ is $T[i,lsp]$. Then the last
@@
 fetching a query result $QB$, the master bitmap is updated by
-$MB = MB \; \& \; QB$, where \& is the bitwised-AND operation. For the
-updated $MB$, if $mb_{lsp-k+1} = 1$, position $i$ is considered as a
-potential matched position and the verification module is
-invoked. Otherwise, the sliding window $W$ is advanced by $lsp-k+1$
-positions if all the bits of $MB$ are 0's, or $lsp-k+1-r$ positions if
-$mb_r=1$ and $mb_i=0$, for $r < i \leq lsp-k$. The positions skipped
-by $W$ are filtered out. If $W$ is determined to be advanced by $h$
-positions, $MB$ is right-shifted by $h$ bits and filled with 1's for
-the holes left by the shift. Particularly, it is proved in
-\cite{Lee2013} that the proposed filter using master bitmap and simple
-bitwised AND and SHIFT operations is optimal in the sense that it is
-able to utilize all previous query results, which means the filter can
-filter out as many positions as possible in the text.
-
-As an example, consider the query bitmaps constructed above and assume
-that $T=23764614621$. Initially, the matching window $W$ contains
-23764 and $MB = 1111$. The last 2-symbol block of $W$, i.e. 64, is
-used for the first query, and the query result is $QB=0010$. Since
-$MB\; \&\; QB = 0010$, $W$ is advanced by 1 position (which means the
-first position of $T$ is filtered out), and then $MB$ is updated as
-$1001$ by right shift. For the second position, the substring
-contained in $W$ is 37646.  This time, block 46 is used to query the
-bitmaps and the query result is $QB=0110$. Since $MB\; \& \; QB=0000$,
-$W$ moves forward by 4 positions to position 6 (which means positions
-$2 \sim 5$ are filled out), and $MB$ is updated as 1111. For position
-6, $W$ contains 61462 and block 62 is used for querying and fetches
-$QB = 0001$. Since $MB\; \& \; QB = 0001$, position 6 is a potential
-matched position, and then the verification module is invoked. After
-checking, the pattern $p_3=614621$ is detected at position 6. Then,
-$W$ is advanced by 4 positions to position 10. However, since the
-length of the remaining input text in $W$, i.e. 21, is smaller than
-$lsp$, which means there can not be any pattern starting at that
-position, the whole scanning procedure is terminated.
-
-% The core idea of the filter is to use the length-$lsp$ prefix of each
-% pattern as the \textsf{signatures}, and then use the signatures to
-% check the validity of each position. In particular, if the current
-% position of the text (roughly) matches a signature, which means the
-% position may match the corresponding pattern, the current position is
-% a potential matched position; otherwise, if the current position does
-% not match any signature, this position can not match any pattern
-% either and can be safely filtered out.
+$MB = MB \; \& \; QB$, where \& is the bit-wised ``and''
+operation. For the updated $MB$, if $mb_{lsp-k+1} = 1$, position $i$
+is considered as a potential matched position and the verification
+module is invoked. Otherwise, the sliding window $W$ is advanced by
+$lsp-k+1$ positions if all the bits of $MB$ are 0's, or $lsp-k+1-r$
+positions if $mb_r=1$ and $mb_i=0$, for $r < i \leq lsp-k$. The
+positions skipped by $W$ are filtered out. If $W$ is determined to be
+advanced by $h$ positions, $MB$ is right-shifted by $h$ bits and
+filled with 1's for the holes left by the shift. Particularly, it is
+proved in \cite{Lee2013} that the filter using master bitmap and
+simple bit-wised ``and'' and ``shift'' operations is optimal in the
+sense that it is able to utilize all previous query results, which
+means the filter can filter out as many positions as possible in the
+text.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=2.5in, width=2.5in]{./eps/filter_match}
+  \caption{Filter the positions in the text using the filter.}
+  \label{fig:f_match}
+\end{figure}
+
+As an example (see Figure \ref{fig:f_match}), consider the query bitmaps
+constructed above and assume that $T=23764614621$.  Initially, the
+matching window $W$ contains 23764 and $MB = 1111$.  The last 2-symbol
+block of $W$, i.e. 64, is used for the first query, and the query
+result is $QB=0010$. Since $MB\; \&\; QB = 0010$, $W$ is advanced by 1
+position (which means the first position of $T$ is filtered out), and
+then $MB$ is updated as $1001$ by right shift. For the second
+position, the substring contained in $W$ is 37646. This time, block 46
+is used to query the bitmaps and the query result is $QB=0110$. Since
+$MB\; \& \; QB=0000$, $W$ moves forward by 4 positions to position 6
+(which means positions $2 \sim 5$ are filled out), and $MB$ is updated
+as 1111. For position 6, $W$ contains 61462 and block 62 is used for
+querying and fetches $QB = 0001$. Since $MB\; \& \; QB = 0001$,
+position 6 is a potential matched position, and thus, the verification
+module is invoked. After checking, the pattern $p_3=614621$ is
+detected at position 6. Then, $W$ is advanced by 4 positions to
+position 10. However, since the length of the remaining input text in
+$W$, i.e. 21, is smaller than $lsp$, which means there can not be any
+pattern starting at that position, the whole scanning procedure is
+terminated.
 
@@
 the pattern set. In the next subsections, we will introduce the
-construction of the AMT, constructed AMT, and a some further
-optimization techniques.
+construction of the AMT and some further optimization techniques.
 
@@
 \begin{enumerate}
-\item Create a suffix set $SF$, and put each pattern of the pattern
+\item Create a suffix set $SF$, and put each pattern in the pattern
   set into $SF$, where each pattern is regarded as a suffix of itself.
@@
   step 2.
-\item Divide $SF$ by putting together all the suffixes with same
+\item Divide $SF$ by putting together all the suffixes with the same
   prefix removed, to form a sub-suffix-set. Associate each
@@
 
-As an example, Figure \ref{fig:AMT} shows of the construction of AMT
-from a pattern set $P = \{p_1,\, p_2,\, \dots,\, p_{13}\}$. Note that,
+As an example, Figure \ref{fig:AMT} shows the construction of AMT from
+a pattern set $P = \{p_1,\, p_2,\, \dots,\, p_{13}\}$. Note that,
 since each pattern is a suffix of itself, the whole pattern set $P$
-can be also regarded as a suffix set $SF$. First, since $p_6$ is the
+can be regarded as a suffix set $SF$.  First, since $p_6$ is the
 shortest pattern(suffix) in $P$, we have $lss = |p_6| = 2$. Then the
@@
 
-The same procedure is repeated upon each of the three created
+The same procedure is repeated on each of the three created
 sub-suffix-sets. As a further example, $SF_1$ of $tp_1$ is
@@
 left: $PF_1 = \{a^6,\, e^6,\, b^6\}$ (we use the notation $c^n$ to
-denote a length-$n$ string consisting of the same character $c$). Then
-a new tree node $node_1$ is built adaptively upon $PF_1$ to hold its
-prefixes as keys.  According to the first component of $tp_1$
+denote a length-$n$ string consisting of the same character $c$).
+Then a new tree node $node_1$ is built adaptively upon $PF_1$ to hold
+its prefixes as keys.  According to the first component of $tp_1$
 (i.e. $root.aa$), $node_1$ is associated with the key $aa$ in the root
@@
 result of this, any path from the root to a key that marked with an
-asterisk represents a complete pattern. From this it can be seen that,
-the patterns are stored implicitly in the AMT and can be reconstructed
+asterisk represents a complete pattern. It can be seen that, the
+patterns are stored implicitly in the AMT and can be reconstructed
 from the paths ended with an asterisk.
@@
 $SF_6$, $\dots$ are processed in sequence. Once there is no tuple left
-in the queue, the whole AMT has been constructed.
+in the queue, the whole AMT has been constructed.  It is worth
+pointing out that, we can also use a depth-first strategy to build the
+AMT branch by branch, but regardless of the strategies used, the final
+built AMTs are the same.
 
@@
 detected by the filter module. The variable $m\_len$ is the total
-length of the sub-strings of the text who have matched with keys in
-AMT nodes. The variable $node$ points to the current searching node in
-the AMT. In addition, since all the keys in a node have the same
-length, the notation $key\_len(node)$ is used to denote the length of
-the keys in $node$.
+length of the sub-strings of the text who have successfully matched
+with keys in AMT nodes. The variable $node$ points to the current
+matching node in the AMT. In addition, since all the keys in a node
+have the same length, the notation $key\_len(node)$ is used to denote
+the length of the keys in $node$.
 
@@
     \ENDIF
-    \STATE $node \leftarrow$ The child of $node.key$
+    \STATE $node \leftarrow$ The child of $node$ corresponding to $node.key$
     \ENDWHILE
@@
 features of the prefix set. Since all the keys in the prefix set have
-the same length, the features of the prefix set can mainly be
+the same length, the features of the prefix set can be mainly
 characterized by two values: the \emph{length} and \emph{number} of
-the keys in the prefix set. These two values are respectively
+the keys in the prefix set. These two values have been respectively
 symbolized by $lss$ and $ndp$ in Section \ref{subsec:amt}.
@@
 
-Given a prefix set, if the length of keys is equal to 1 ($lss=1$),
-i.e. each key in the prefix set is just a single character, the
-space-efficient \emph{character map} structure, which was proposed by
-Leis \cite{Leis2013}, will be adopted as the tree node. There are four
-sub-types of character maps with different capacities for different
-number of keys ($ndp$), where $1 \leq ndp \leq 256$.
-
-\begin{figure}[htbp]
+Given a prefix set, if the length of prefixes (keys) is equal to 1
+($lss=1$), i.e. each key in the prefix set is just a single character,
+the space-efficient \emph{character map} structure, which was proposed
+by Leis \cite{Leis2013}, will be adopted as the tree node. There are
+four sub-types of character maps with different capacities for
+different number of keys ($ndp$), where $1 \leq ndp \leq 256$.
+
+\begin{figure}[hp]
   \centering
-  \includegraphics[width=0.75\textwidth]{./eps/Maps}
+  \includegraphics[height=3.5in, width=3.5in]{./eps/Maps}
   \caption{The four sub-types of character maps. The triangles
@@
 the Map 4 and Map 16 structures, the keys are stored in
-lexicographical order in a separate key array of $ndp \times lss$
+lexicographical order in a separate key array with $ndp \times lss$
 bytes, in which each key takes $lss$ bytes. The child pointers are
@@
 task, the hash function is selected randomly from a \emph{hash
-  function family} $H$. The hash function family adopted in our
-implementation is the fast \emph{shift-add-xor} hash family proposed
-by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
-uniform and universal. The framework of the hash function family is
-shown in Algorithm \ref{alg:hash fun}.
-
-%  satisfied with the
-% \textsf{uniformity}, \textsf{universality}, \textsf{applicability} and
-% the \textsf{efficiency} properties
-
-%  which should satisfy the following properties:
-
-% \begin{itemize}
-% \item \textbf{Uniformity.} If a hash function is uniform then the
-% probability of an arbitrary key hashing to a given slot is
-% $1/table\_size$, independent of the hash values of other keys. In
-% practical terms, uniformity means that for a given load factor average
-% access time is roughly constant, regardless of table size.
-
-% \item {Universality.} A hash function family $H$ is universal
-% if, for a given $table\_size$ and any pair of valid keys $k_1$ and
-% $k_2$, the number of hash functions $h \in H$ such that $h(k_1) =
-% h(k_2)$ is less than or equal to $|H|/table\_size$. That is, for a
-% randomly-chosen hash function the probability that $k_1$ and $k_2$
-% hash to the same value is less than or equal to $1/table\_size$.
-
-% In practice universality means that, with high probability, a
-% randomly-chosen hash function will perform well. For any hash function
-% it is true that there exist sets of keys that all hash to the same
-% value and no hash function is invulnerable to a deliberate attempt to
-% identify such a set of keys. However, if a hash function family is
-% universal and the functions in the family are uniform then it is
-% guaranteed that the family cannot be subjected to such attack.
-
-% \item {Applicability.} At a more pragmatic level, hash
-% functions should be applicable in all circumstances where hashing
-% might be used. A function that is limited to a few table sizes, can
-% only hash strings of a certain length, is not as valuable as functions
-% without such restrictions.
-
-% \item {Efficiency}. The primary advantage of hashing as an
-% access method is its speed: given $ndp$ keys and a table of $O(ndp)$
-% size, the search time is $O(1)$, assuming a hash function with time
-% complexity $O(1)$. Hash functions should also be small; in many
-% applications there is little advantage to a function that is as large
-% as the key set.
-
-\begin{algorithm}
-  \caption{The \textsf{shift-add-xor} hash family}\scriptsize
-  \label{alg:hash fun}
-  \begin{algorithmic}[1]
-    \REQUIRE ~~\\
-    The string $c_1c_2 \dots c_m$ and the $table\_size$.  \\
-    \ENSURE ~~\\
-    The hash value of $c_1c_2 \dots c_m$.
-    \STATE
-    \STATE $value \leftarrow seed$
-    \FOR{$i \leftarrow 1$ to $m$}
-    \STATE $value \leftarrow value \oplus (value << L + value >> R + c_i)$
-    \ENDFOR
-    \RETURN $value$ mod $table\_size$
-  \end{algorithmic}
-\end{algorithm}
-
-Firstly, a random positive integer $seed$ is assigned to the initial
-$value$ of the hash function. (Note that, different seeds give
-different hash functions, consequently, a hash function family can be
-defined by given different seeds.) Then the hash value is computed
-gradually from each character of the input string, by using the
-combinations of the \textsf{add, shift, xor} operators. In particular,
-$\oplus$ is the \textsf{xor} operator, $value << \;L$ ($value >> \;R$)
-means shift the $value$ to the left (right) $L$ ($R$) bits and $c_i$
-is the ASCII value of the $i$-th character of the input
-string. Through testing, we set $L=5$ and $R=2$ in our experiment,
-which is able to provide greater likelihood of a uniform distribution
-of hash values.
+  function family} $H$. The hash function family we adopted is the
+fast \emph{shift-add-xor} hash family proposed by Ramakrishna
+\cite{Ramakrishna1997}, which is claimed to be both uniform and
+universal.
 
@@
 $P=\{p_1=e^6u^5sscc,\; p_2=e^6u^5,\; p_3=e^6\}$ and the corresponding
-AMT constructed by Algorithm 1. As shown in Fig (a), the built AMT has
-three nodes, and each contains only one key. In a typical x86\_64
-architecture, this implementation of AMT roughly takes 55 bytes of
-memory: 15 bytes for the three keys, 16 bytes for the two child
-pointers and 24 bytes for the three pointers to the matching
+AMT constructed by Algorithm 1. As shown in Figure \ref{fig:merge}, the
+built AMT has three nodes, and each contains only one key. In a
+typical x86\_64 architecture, this implementation of AMT takes roughly
+55 bytes of memory: 15 bytes for the three keys, 16 bytes for the two
+child pointers and 24 bytes for the three pointers to the matching
 functions. However, if we combine the three keys into one string,
-these three nodes can be merged into one node (Fig (b)), as a result,
-the child pointers are no longer needed and the number of function
-pointers is reduced from three to one. The merged node is another type
-of tree node in addition to the node types we have introduced in
-Section \ref{subsec:nodes}.
+these three nodes can be merged into one node, as a result, the child
+pointers are no longer needed and the number of function pointers is
+reduced from three to one. The merged node is another type of tree
+node in addition to the node types we have introduced in Section
+\ref{subsec:nodes}.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=2in, width=2in]{./eps/node_merge}
+  \caption{Node merging.}
+  \label{fig:merge}
+\end{figure}
 
 For the merged node, the only problem is how to distinguish among the
-keys after they are concatenated, to address this issues, a
+keys after they are concatenated. To address this issue, a
 \emph{length array} is used to store the length of each key, where
@@
 type). Through the length of each key, we can delimit each original
-keys, and thus, searching the target string in the merged node can be
-trivial.
+key from others, and thus, searching the target string in the merged
+node can be trivial.
 
@@
 
-Once the keys in a node share a common prefix, that prefix can be
-removed from the keys and form a new single key node (since the prefix
-is either a character or a string, the type of the new node is either
-Map 4 or String Array). This technique can reduce a lot of redundant
-comparisons while searching a target key in that node. For instance,
-consider the node in Fig whose four keys share a common prefix $a^4$,
-and a target key which is $a^4u$. it will be compared with the four
-keys in order and finally takes $5 \times 4 = 20$ byte comparisons to
-determine the inexistence of target key. However, if $a^4$ is split
-out and form another new node as shown in Fig , for the same target,
-only 8 byte comparisons (4 comparisons for $node_1$ and another 4
-comparisons for $node_2$) is needed.
+In order to further improve the searching efficiency of the tree
+nodes, once the keys in a node share a common prefix, that prefix
+should best be removed from the keys and form a new single key node
+. (Note that, since the prefix is either a character or a string, the
+type of the new created node is either Map 4 or String Array.)  This
+action can reduce a lot of redundant comparisons while searching a
+target key in a node. For instance -- as shown in Figure \ref{fig:split},
+consider searching a target key $a^5u$ in a node of String Array type,
+where the four keys of the node share a common prefix $a^5$. According
+to Algorithm \ref{alg:string array}, the target key have to be
+compared sequentially with the four keys, which will totally takes
+$6 \times 4 = 24$ byte comparisons to determine the inexistence of
+target key. However, if the common prefix $a^5$ is removed out of the
+keys and form another new node as shown in Figure \ref{fig:split}, for
+the same target key, only 9 byte comparisons are needed for verifying
+(5 comparisons for $node_1$ and another 4 comparisons for
+$node_2$). Obviously, comparing with only one node, the two nodes
+version can reduce 15 comparisons.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=2.5in, width=2in]{./eps/node_split}
+  \caption{Node splitting.}
+  \label{fig:split}
+\end{figure}
 
@@
 
-In this section, we evaluate the performance of \textsf{AAMPM}, and
-compare it with other four algorithms: the \textsf{AC} and \textsf{WM}
+In this section, we evaluate the performance of the proposed fast
+engine for multi-pattern matching (\textsf{FEMPM} for short), and
+compare it with other five algorithms: the \textsf{AC} and \textsf{WM}
 algorithms, which are two classic ``baseline'' algorithms for MPM; the
-\textsf{MASM} and \textsf{Pre-filter+AC} algorithms, which are two
-state-of-the art MPM algorithms with good efficiency in practically
-matching. All these algorithms are evaluated in two aspects: the
+\textsf{Split}, \textsf{MASM} and \textsf{Pre-filter+AC} algorithms,
+which are three state-of-the-art MPM algorithms with good efficiency
+in practice. All these algorithms are evaluated in two aspects: the
 robustness of these algorithms under pattern sets with various $lsp$s
 and the scalability of the algorithms under pattern sets with various
-number of patterns.
+numbers of patterns.
 
@@
 experiments is the real-world English text from the Pizza\;\&\;Chili
-corpus. The patterns are extracted randomly from the text to form the
-pattern sets.
-
-Next, the parameter configuration in \textsf{AAMPM} in our experiment
-are given. For the String Arrays, if the number of strings exceeds
-\textbf{4}, the binary search is used to search the target string in
-the key array; otherwise, the linear search is adopted. For the Hash
-Tables, the load factor is set to \textbf{0.5}; the \emph{seed} of the
-hash function is generated randomly in the range of
-$\mathbf{1} \sim \mathbf{50}$; the shift values \emph{L} and \emph{R}
-are set to \textbf{2} and \textbf{6} respectively. Once the $ndp$ is
-lager than \textbf{100}, the Hash Table is built instead of the String
-Array. These choices of parameters have been extensively tested on a
-wide range of pattern sets, and are considered to be very efficient
-for a typical match.
-
-% The data sets include three kinds of data: the real-world English
-% text and the DNA sequence from the Pizza\&Chili corpus, the random
-% string which is generated artificially.
-
-\subsection{Evaluation under various lsps}
+corpus \cite{pizzachil}. The patterns are extracted randomly from the
+text to form the pattern sets.
+
+Next, the parameter configuration of \textsf{FEMPM} in the experiment
+is given as follows: for the String Arrays, if the number of strings
+exceeds \textbf{4}, the binary search is used to search the target
+string in the key array; otherwise, the linear search is adopted (for
+String Arrays containing no more than 4 strings, the simple linear
+search is faster than binary search due to the complexity of binary
+search). For the Hash Tables, the load factor is set to be
+\textbf{0.5}, which is a good balance between time and space; the seed
+of the hash function is generated randomly in the range of 1~50; the
+shift values L and R are set to \textbf{2} and \textbf{6} respectively
+(the parameters about the hash function are chosen from
+\cite{Ramakrishna1997} which are claimed to be very efficient). Once
+the $ndp$ is larger than \textbf{100}, the Hash Table becomes more
+efficient than the String Array, thus the Hash Table is built once
+$ndp>100$. These choices of parameters have been extensively tested on
+a wide range of pattern sets, and are considered to be very efficient
+in practice.
+
+\subsection{Robustness Evaluation}
 
 As we've mentioned before, many MPM algorithms are sensitive to the
-length of the patterns, particularly, the length of the shortest
-pattern ($lsp$) in the pattern set. Therefore, it is necessary to
-measure the performance of the \textsf{AAMPM} and compare it with the
-other investigated algorithms under pattern sets with various
-$lsp$s. In this evaluation, there are totally 9 pattern sets for
-testing with $lsp$s ranging from 2 to 10, and every pattern set has a
-fixed number of $10^5$ patterns. The size of text string is fixed to
-200 MB. The characteristics of the pattern sets are shown in Table
+length of the shortest pattern ($lsp$) in the pattern set. So first,
+it is necessary to measure the robustness of \textsf{FEMPM} and other
+investigated algorithms under pattern sets with various $lsp$s. In
+this evaluation, there are totally 9 pattern sets for testing with
+$lsp$s ranging from 2 to 10, and each pattern set has a fixed number
+of $10^5$ patterns. The size of text string is fixed to 200 MB. The
+characteristics of the testing pattern sets are shown in Table
 \ref{tab:lsps}, which includes: the length of the shortest pattern
@@
 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[height=2in, width=2.5in]{./eps/lsp}
+  \caption{Matching times for various lsp.}
+  \label{fig:lsp}
+\end{figure}
+
 \begin{table}
@@
   \label{tab:lsps}
-  \begin{tabular}{rrrrrrr}
+  \begin{tabular}{p{20pt}p{10pt}p{10pt}p{10pt}p{10pt}p{30pt}p{20pt}}
     \hline
@@
 
-% For universality, evaluation are performed independently on three
-% different kinds of data: the English text, the DNA sequence and the
-% random string. These three types of data have completely different
-% alphabet and character combination. Therefore this evaluation can
-% reflect the robustness of the algorithms for pattern sets with
-% various features.
-
-% The performance of the investigated algorithms are measured in
-% preprocessing time and the matching time. The former is the time
-% consumed by constructing the data structure in the preprocessing
-% phase; the latter is used for matching with the text string in the
-% matching phase. Usually, most of the algorithms mainly focus on the
-% matching time, however, the preprocessing time is also significant
-% factor, since a very short preprocessing time means the algorithm
-% allows the pattern set to be updated dynamically.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.6\textwidth]{./eps/lsp}
-  \caption{Matching times for various lsps.}
-  \label{fig:lsp}
-\end{figure}
-
 Figure \ref{fig:lsp} presents the mean matching time (in seconds) used
 by these algorithms based on 5 independent runs. In general, the
-\textsf{AC} algorithm is not affected much by the changes in $lsp$.
-However, the DFA built by this algorithm consumes a huge amount of
-memory. What's worse is that, the frequent, unpredictable
+\textsf{AC} algorithm is not affected much by the changes in
+$lsp$. However, the DFA built by this algorithm consumes a huge amount
+of memory. What's worse is that, the frequent and unpredictable
 state/failure transitions will lead to a lot of cache misses during
-matching, and these results in the low performance of \textsf{AC}. The
-\textsf{WM} algorithm outperforms \textsf{AC} on the pattern sets
-whose $lsp$ is larger than 2, even so, for the pattern sets with small
+matching, and these result in the low performance of \textsf{AC}. On
+the other side, the \textsf{Split} algorithm, which is also based on
+DFA, is not effected much by $lsp$, and since it extracts a subset of
+unique patterns to build the DFA and uses a bit-split technique, the
+memory and time consumption are greatly reduced. It can be seen from
+Figure \ref{fig:lsp} that the \textsf{WM} algorithm is affected much
+by the changes in $lsp$: it outperforms \textsf{AC} on the pattern
+sets whose $lsp$ is larger than 2, but for the pattern sets with small
 $lsp$, the performance of \textsf{WM} degrades dramatically. This is
@@
 work well for the pattern sets with small $lsp$s, which means most of
-the positions in the text need to be checked by the HASH table of
-\textsf{WM}, and this takes a lot of time. The \textsf{Pre-filter+AC}
-algorithm outperforms all other algorithms (except \textsf{AAMPM}) for
-pattern sets whose $lsp$ is larger than 4. Similarly, this algorithm
-also uses a skip strategy: once a position of the text is filtered out
-by the Pre-filter, at most the following $lsp-1$ positions can be
-skipped over. Consequently, for pattern sets with small $lsp$, this
-algorithm can not skip much in the text, which will seriously affect
-its performance. In contrast, the \textsf{MASM} algorithm performs
-well for small $lsp$ ($lsp \leq 4$). This algorithm first compacts the
-pattern set by a prefix tree: if a pattern $A$ is a prefix of another
-pattern $B$, $A$ can be merged into $B$. Then the algorithm builds a
-binary search tree for the compacted pattern set based on
-lexicographical order. Comparing with the long patterns, the short
-ones are more likely to be prefixes of others, and thus, more likely
-to be eliminated by compacting. Thus, pattern sets with small $lsp$
-are well compressed, which will improve both time and space efficiency
-of \textsf{MASM} in the matching phase.
-
-From Figure \ref{fig:lsp} we can see that, \textsf{AAMPM} outperforms
-all other investigated algorithms on every $lsp$. Comparing with
-\textsf{AC}, the matching time is reduced by $85\%$ in average for all
-$lsp$s; even comparing with the fast \textsf{Pre-filter+AC} algorithm,
-the matching time is reduced by $10\% \sim 20\%$ for medium $lsp$s
-($lsp \geq 4$) and by $70\%$ for small $lsp$s ($lsp < 4$). As
-mentioned before, this is mainly due to the adaptivity of the nodes of
-AMT, which enables the tree nodes as efficient and compact as
-possible. Therefore, no matter what the $lsp$s of the pattern sets
-are, the corresponding AMT is able to keep high search efficiency as
-well as low memory requirement in the matching phase. Owing to this,
-the \textsf{AAMPM} has the best robustness for all of the testing
-pattern sets. The statistics about node types of corresponding AMTs
-are shown in table \ref{tab:node types}. The Single Char and Single
-String types in the table are actually the Map 4 and String Array
-types which contain only one element, respectively. Obviously, as the
-$lsp$ of the pattern set changes, the number of nodes of the each type
-in the AMT changes accordingly, which reflects the adaptivity of AMT.
-
-Moreover, the performance of \textsf{AAMPM} is very stable and
+the positions in the text string need to be checked by the HASH table
+of \textsf{WM}, and this takes a lot of time. The
+\textsf{Pre-filter+AC} algorithm outperforms all other algorithms
+except for \textsf{FEMPM} for pattern sets whose $lsp$ is larger than
+5. Similarly, this algorithm also uses a skip strategy: once a
+position of the text string is filtered out by the Pre-filter, at most
+the following $lsp-1$ positions can be skipped over. Consequently, for
+pattern sets with small $lsp$, this algorithm can not skip much in the
+text string, which will seriously affect its performance. In contrast,
+the \textsf{MASM} algorithm performs well for small $lsp$
+($lsp \leq 4$). This algorithm first compacts the pattern set by a
+prefix tree: if a pattern $A$ is a prefix of another pattern $B$, $A$
+can be merged into $B$. Then the algorithm builds a binary search tree
+for the compacted pattern set based on lexicographical
+order. Comparing with the long patterns, the short ones are more
+likely to be prefixes of others, and thus, more likely to be
+eliminated by compacting. Thus, pattern sets with small $lsp$ are well
+compressed, which will improve both time and space efficiency of
+\textsf{MASM} in the matching phase.
+
+From Figure \ref{fig:lsp} we can also see that, \textsf{FEMPM}
+outperforms all other investigated algorithms on every
+$lsp$. Comparing with \textsf{AC}, the matching time is reduced by
+$85\%$ in average for all $lsp$s; even comparing with the fast
+\textsf{Pre-filter+AC} algorithm, the matching time is reduced by
+$10\% \sim 20\%$ for medium $lsp$s ($lsp \geq 4$) and by $70\%$ for
+small $lsp$s ($lsp < 4$). Although the filter part of \textsf{FEMPM},
+which likes that of \textsf{Pre-filter+AC}, is not suitable for small
+$lsp$, the verification part, i.e. AMT, is more efficient than that of
+the \textsf{Pre-filter+AC}. This is mainly due to the adaptivity of
+the nodes of AMT, which enables the tree nodes as efficient and
+compact as possible. Therefore, no matter what the $lsp$s of the
+pattern sets are, the corresponding AMT is able to keep high search
+efficiency as well as low memory requirement in the verification
+phase. Owing to this, the \textsf{FEMPM} has the best robustness for
+all of the testing pattern sets. The statistical data about node types
+of corresponding AMTs are shown in table \ref{tab:node types}. The Map
+1 and Single String Array types in the table are actually the Map 4
+and String Array types which contain only one element,
+respectively. Obviously, as the $lsp$ of the pattern set changes, the
+number of nodes of the each type in the AMT changes accordingly, which
+reflects the adaptivity of AMT.
+
+Moreover, the performance of \textsf{FEMPM} is very stable and
 reliable. In particular, once the length of the text and number of
@@
 $lsp$s. As shown in Figure \ref{fig:lsp}, the matching time of
-\textsf{AAMPM} is always about 10 seconds for a text of 200MB and a
-pattern set with $10^5$ patterns; for $lsp$s ranging from $2$ to $10$,
-the change in the matching time is less than 2 seconds. In fact, as
-the $lsp$ increases, the average length of the paths from the root to
-the leaves in AMT will increase slightly. Accordingly, in the matching
-phase, the matching paths for some text positions may get a little
-longer, which might slightly slow down the matching speed.
-
-% Since these volumes are all fixed in this evaluation, the matching
-% time is nearly the same under all lsps.
+\textsf{FEMPM} keeps almost 10 seconds unchanged for a text of about
+200MB and a pattern set with about $10^5$ patterns; for $lsp$s ranging
+from $2$ to $10$, the change in the matching time is less than 2
+seconds. In fact, as the $lsp$ increases, the average length of the
+paths from the root to the leaves in AMT will increase
+slightly. Accordingly, in the matching phase, the matching paths for
+some text positions may get a little bit longer, which might slightly
+affect the matching speed.
 
@@
   \label{tab:node types}
-  \begin{tabular}{rrrrrrrrrr}
+  \begin{tabular}{p{10pt}p{15pt}p{15pt}p{15pt}p{15pt}p{15pt}p{25pt}p{25pt}p{20pt}p{25pt}}
  \hline
  Lsp &
- Single Char &
+ Map 1 &
  Map 4 &
@@
  Map 256 &
- Single String &
+ Single String Array &
  String Array   &
@@
 
-\subsection{Evaluation under various numbers of patterns}
+\subsection{Scalability Evaluation}
 
@@
 algorithms by testing them under pattern sets with various numbers of
-patterns. As before, the size of the text is fixed to 200MB, and there
-are two groups of pattern sets for testing --- the small group and the
-large group. The small group contains 9 pattern sets, with the sizes
-(number of patterns) increasing from $1 \times 10^5$ to
-$9 \times 10^5$ in steps of $10^5$, while the large group contains 10
-pattern sets, with the sizes increasing from $10^6$ to $10^7$ in steps
-of $10^6$. The range of the pattern length of each pattern set is
-fixed to $5 \sim 50$.
+patterns. As before, the size of the text string is fixed to 200MB,
+and there are two groups of pattern sets for testing --- the small
+group and the large group. The small group contains 9 pattern sets,
+and the sizes (number of patterns) of the pattern sets increase from
+$1 \times 10^5$ to $9 \times 10^5$ with step size of $10^5$, while the
+large group contains 10 pattern sets, and the sizes increase from
+$10^6$ to $10^7$ with step size of $10^6$. The range of the pattern
+length of each pattern set is fixed to $5 \sim 50$.
 
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{./eps/small_group}
+  \includegraphics[height=2in, width=2.5in]{./eps/small_group}
   \caption{Matching times for the small group.}
@@
 \ref{fig:small_group}. The experimental results indicate that, the
-performance of the \textsf{AC} algorithm is relative stable (but not
-high) as the number of patterns growing, but it can not deal with
+performance of the \textsf{AC} algorithm is not good but relative
+stable with the number of patterns growing. Also it can not deal with
 pattern sets whose size is larger than $7 \times 10^5$ in this testing
-due to lack of memory. Although the \textsf{WM} algorithm performs
-better than \textsf{AC}, it is less stable, for instance, the matching
-time only rises about $1s$ as the number of patterns increasing from
-$2 \times 10^5$ to $3 \times 10^5$, but when the number of patterns
-increases from $8 \times 10^5$ to $9 \times 10^5$, the matching time
-rises up to $9s$. Thus, we can not estimate the matching time of
-\textsf{WM} based on the size of the pattern set. The
-\textsf{Pre-filter+AC} performs well as the number of patterns
-growing, but its matching time is also unpredictable, e.g. the
-matching times are nearly the same as the number of patterns
-increasing from $4 \times 10^5$ to $5 \times 10^5$. The instability of
-\textsf{WM} and \textsf{Pre-filter+AC} is mainly due to that: the
-effect of the filters used by these two algorithms highly depends on
-the contents of the text and patterns themselves, for some pattern
-sets whose patterns occurs frequently in the text, the effect of the
+, due to out of memory. Although the \textsf{WM} algorithm performs
+better than \textsf{AC}, its performance is not stable. For instance,
+the matching time only rises about $1s$ as the number of patterns
+increases from $2 \times 10^5$ to $3 \times 10^5$, but when the number
+of patterns increases from $8 \times 10^5$ to $9 \times 10^5$, the
+matching time rises up to $9s$. Thus, we can not estimate the matching
+time of \textsf{WM} based on the size of the pattern set. The
+\textsf{Pre-filter+AC} performs well as the number of patterns grows,
+but its matching time is also unpredictable, e.g. the matching times
+are nearly the same as the number of patterns increases from
+$4 \times 10^5$ to $5 \times 10^5$. The reason is that: the effect of
+the filters used by these two algorithms highly depends on the
+contents of the text and patterns themselves. For some pattern sets
+whose patterns occurs frequently in the text, the effect of the
 filters degrades. On the other hand, as the number of patterns grows,
@@
 search tree and that depth grows very slow as the number of patterns
-increasing.
-
-% For the \textsf{MASM} algorithm, its
-% performance is more stable than the \textsf{Pre-filter+AC} algorithm.
-% This is because the performance of \textsf{MASM} mainly relies on the
-% depth of the pipelined binary search tree, which  as the
-% number of patterns increases.
+increases. The \textsf{Split} algorithm performs very well for the
+small group of patterns, it is only $10\% \sim 20\%$ slower than our
+\textsf{FEMPM}.
 
@@
   \scriptsize
-  \caption{The statistics about the AMTs for the small group}
+  \caption{The statistics about the node type in AMTs built for the small group}
   \label{tab:small}
-  \begin{tabular}{rrrrrrrrrr}
+  \begin{tabular}{p{25pt}p{25pt}p{25pt}p{25pt}p{15pt}p{15pt}p{25pt}p{25pt}p{20pt}p{25pt}}
  \hline
  Size &
- Single Char &
+ Map 1 &
  Map 4 &
@@
 
-Among all these algorithms, the \textsf{AAMPM} is the most efficient
-as well as stable one. The high performance of \textsf{AAMPM} is
+Among all these algorithms, the \textsf{FEMPM} is the most efficient
+as well as stable one. The high performance of \textsf{FEMPM} is
 mainly due to the \emph{root} node of AMT, which is almost always the
 Hash Table as the number of patterns grows. As mentioned before, the
-root plays the role of a ``filter'', by which a large number of
-positions of the text that are impossible to match with any pattern
-can be quickly filtered out. Moreover, the increasing in the number of
-patterns mainly leads to the growing of the width rather than the
-depth of AMT. Therefore, for each position of the text, the checking
-time changes slightly. From the experimental results, we can even give
-a rough estimate on the matching time based on the size of pattern set
-as follows: given the text of 200 MB, an increase of $10^5$ in the
-number of patterns will lead to roughly $1$ more second taken in the
-matching time. The statistics about the node types of the
-corresponding AMTs for the small group are shown in Table
+root plays the role of another ``filter'', by which a large number of
+positions of the text that can not be filtered by the filter part may
+have a chance to be filtered out by the root. Moreover, the increasing
+in the number of patterns mainly leads to the growing of the width
+rather than the depth of AMT. Therefore, for each position of the
+text, the checking time changes slightly. From the experimental
+results, we can even give a rough estimate on the matching time based
+on the size of pattern set as follows: given the text of 200 MB, an
+increase of $10^5$ in the number of patterns will lead to roughly $1$
+more second taken in the matching time. The statistics about the node
+types of the corresponding AMTs for the small group are shown in Table
 \ref{tab:small}. We can see that an increase of $10^5$ in the number
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{./eps/large_group}
+  \includegraphics[height=2in, width=2.5in]{./eps/large_group}
   \caption{Matching times for the large group.}
@@
 For the large group, the mean matching times of the investigated
-algorithms are shown in Figure \ref{fig:large_group}.  From the
-results we can see that, as the number of patterns grows from $10^6$
-to $10^7$, the increases in the matching time of the investigated
-algorithms are: $410\%$ (\textsf{WM}), $374\%$
-(\textsf{Pre-filter+AC}), $238\%$ (\textsf{MASM}), $112\%$
-(\textsf{AAMPM}) respectively. For every increase of $10^6$ in the
-number of patterns, the mean increment in the matching time of the
-investigated algorithms are: $23.7s$ (\textsf{WM}), $17.0s$
-(\textsf{Pre-filter+AC}), $12.3s$ (\textsf{MASM}), $3.5s$
-(\textsf{AAMPM}) respectively. From the results we can see that,
-\textsf{Pre-filter+AC} and \textsf{WM} perform not well for large
-pattern sets. This is because, as the number of patterns grows, the
-chances for every position of the text to successfully match a pattern
-increases, which will reduce the effect of the filters of these
-algorithms and results in performance degradation. The \textsf{MASM}
-algorithm outperforms \textsf{Pre-filter+AC} for pattern sets whose
-size are larger than $3 \times 10^6$, which is due to its pattern set
-compression strategy and the good scalability of its pipelinded binary
-search tree.
+algorithms are shown in Figure \ref{fig:large_group}. It can be seen
+that, as the number of patterns grows from $10^6$ to $10^7$, the
+increases in the matching time of the investigated algorithms are:
+$410\%$ (\textsf{WM}), $374\%$ (\textsf{Pre-filter+AC}), $238\%$
+(\textsf{MASM}), $191\%$ (\textsf{Split}), $112\%$ (\textsf{FEMPM})
+respectively. For every increase of $10^6$ in the number of patterns,
+the mean increment in the matching time of the investigated algorithms
+are: $23.7s$ (\textsf{WM}), $17.0s$ (\textsf{Pre-filter+AC}), $12.3s$
+(\textsf{MASM}), $8.8s$(\textsf{Split}), $3.5s$ (\textsf{FEMPM})
+respectively. This indicates that, \textsf{Pre-filter+AC} and
+\textsf{WM} perform not well for large pattern sets. This is because,
+as the number of patterns grows, the chances for every position of the
+text to successfully match a pattern increases, which will reduce the
+effect of the filters of these algorithms and results in performance
+degradation. The \textsf{MASM} algorithm outperforms
+\textsf{Pre-filter+AC} for pattern sets whose size are larger than
+$3 \times 10^6$, which is due to its pattern set compression strategy
+and the good scalability of its pipelinded binary search tree. The
+\textsf{Split} algorithm has a better scalability than others (except
+\textsf{FEMPM}), this is because it only extracts a subset from the
+whole pattern set, in which a pattern is not a suffix of any other
+patterns, to build the DFA.
 
 \begin{table}[!htp]
-  \caption{The statistics about the AMTs for the large group}
+  \caption{The statistics about the node type in the AMTs built for
+    the large group}
   \scriptsize
   \label{tab:large_group}
-  \begin{tabular}{rrrrrrrrrr}
+  \begin{tabular}{p{25pt}p{25pt}p{25pt}p{25pt}p{20pt}p{10pt}p{30pt}p{30pt}p{20pt}p{25pt}}
  \hline
  Size &
- Single Char &
+ Map 1 &
  Map 4 &
@@
 
-On the other hand, among all the algorithms, \textsf{AAMPM} is the
+On the other hand, among all the algorithms, \textsf{FEMPM} is the
 most efficient algorithm for large pattern sets. An increase of $10^6$
-in the number of patterns, only require 3 more seconds to match, this
-is mainly due to the good scalability of the AMT which enables the
-matching time grows very slow as the number of patterns explodes. The
-statistics about the AMTs for the large group are shown in Table
-\ref{tab:large_group}. Every $10^6$ increase in the number of patterns
-will increase only about $8 \times 10^5$ tree nodes.
+in the number of patterns, only requires 2.8 more seconds to match,
+this is mainly due to the good scalability of the AMT which enables
+the matching time grows very slow as the number of patterns
+explodes. The statistical data about the AMTs for the large group are
+shown in Table \ref{tab:large_group}. Every $10^6$ increase in the
+number of patterns will increase only about $8 \times 10^5$ tree
+nodes.
 
@@
 
-In this paper, we propose an Adaptive Architecture for Multi-Pattern
-Matching (\textsf{AAMPM}). The \textsf{AAMPM} used a data structure
-called Adaptive Matching Tree (AMT) which can be constructed to fit
-the feature of the given pattern set. Using the AMT to match with the
-text can improve the robustness of \textsf{AAMPM} for pattern sets
-with various $lsp$s. Moreover, owing to the scalability and
-compactness of AMT, \textsf{AAMPM} offers a good support for
-large-scale pattern sets. In the future, we will try to design more
-efficient inner structures of the tree nodes; furthermore, since
-\textsf{AAMPM} needs to check every position of the text string, we
-will further improve this by designing a ``skip scheme'' for
-\textsf{AAMPM}.
+In this paper, we propose a Fast Engine for Multi-Pattern Matching
+(\textsf{FEMPM}) which includes a filter part and a verification
+part. The filter part is used to quickly filter out the positions that
+are impossible to match any pattern, while the verification part is
+used to verify the potential positions. The verification part used a
+data structure called Adaptive Matching Tree (AMT) which can be
+constructed to fit the feature of the given pattern set. Owing to the
+scalability and compactness of AMT, \textsf{FEMPM} offers a good
+support for large-scale pattern sets. Moreover it can improve the
+robustness of \textsf{FEMPM} for pattern sets with various $lsp$s. In
+the future, we will try to design more efficient inner structures of
+the tree nodes.
 
@@
 This work is supported by National Natural Science Foundation of China
-(No.61472297).
-
-\bibliography{./DM}
+(No.61472297) and the Fundamental Research Funds for the Central
+Universities (BDZ021430).
+
+\begin{thebibliography}{99}
+
+\bibitem{Yan2016} Yan, Ruoyu. ``Combining Renyi Entropy and EWMA to
+  Detect Common Attacks in Network'' {\it International Journal of
+    Pattern Recognition and Artificial Intelligence}, 30(10),
+  pp.1650021, 2016.
+
+\bibitem{Xue2015} Xue, Xingsi and Wang, Yuping, ``Optimizing ontology
+  alignments through a Memetic Algorithm using both MatchFmeasure and
+  Unanimous Improvement Ratio'', {\it ARTIFICIAL INTELLIGENCE}, 223,
+  pp.65-81, 2015.
+
+\bibitem{Xue2016} Xue, Xingsi and Wang, Yuping, ``Using Memetic
+  Algorithm for Instance Coreference Resolution'', {\it IEEE
+    TRANSACTIONS ON KNOWLEDGE AND DATA ENGINEERING}, 223, pp.65-81,
+  2015.
+
+\bibitem{Kim2015} Kim, HyunJin and Choi, Kang-Il and Choi, Sang-Il,
+  ``A Memory-Efficient Deterministic Finite Automaton-Based Bit-Split
+  String Matching Scheme Using Pattern Uniqueness in Deep Packet
+  Inspection'', {\it PLOS ONE}, 10(5), 2015.
+
+\bibitem{Xiao2016} Guoqing Xiao, Kenli Li, Xu Zhou, Keqin
+  Li. ``Queueing Analysis of Continuous Queries for Uncertain Data
+  Streams Over Sliding Windows'' {\it International Journal of Pattern
+    Recognition and Artificial Intelligence}, 30(9), pp.1660001, 2016.
+
+\bibitem{Wu1994} Sun Wu and Udi Manber, ``A fast algorithm for
+  multi-pattern searching'', {\it Technical Report-94-17}, 1994.
+
+\bibitem{Lee2013} Tsern-Huei Lee and Nai-Lun Huang, ``A
+  pattern-matching scheme with high throughput performance and low
+  memory requirement'', {\it IEEE/ACM Transactions on Networking},
+  21(4), pp.1104--1116, 2013.
+
+\bibitem{Aho1975} Alfred V. Aho and Margaret J. Corasick, ``Efficient
+  string matching:An aid to bibliographic search'', {\it Commun. ACM}
+  18(6), pp.333-340, 1975.
+
+\bibitem{Knuth1977} Donald E. Knuth, Jr. James H. Morris, and Vaughan
+  R. Pratt, ``Fast pattern matching in strings'', {\it SIAM Journal on
+    Computing}, 6(2), pp.323–350, 1977.
+
+\bibitem{Boyer1977} Robert S. Boyer and J. Strother Moore, ``A fast
+  string searching algorithm'', {\it Commun. ACM}, 20(10), pp.762–772,
+  1977.
+
+\bibitem{Zhang2016} Lungan Zhang, Liangxiao Jiang, Chaoqun Li. ``A New
+  Feature Selection Approach to Naive Bayes Text Classifiers'' {\it
+    International Journal of Pattern Recognition and Artificial
+    Intelligence}, 30(9), pp.1650003 2016.
+
+\bibitem{Tang2015} Guoyu Tang, Yunqing Xia, Erik Cambria, Peng Jin,
+  Thomas Fang Zheng. ``Document Representation with Statistical Word
+  Senses in Cross-Lingual Document Clustering'' {\it International
+    Journal of Pattern Recognition and Artificial Intelligence},
+  30(9), pp.1559003, 2015.
+
+\bibitem{Tuck2004} N. Tuck, T. Sherwood, B. Calder, and G. Varghese,
+  ``Deterministic memory-efficient stringmatching algorithms for
+  intrusion detection'', {\it Twenty-third AnnualJoint Conference of
+    the IEEE Computer and Communications Societies}, Vol 4,
+  pp.2628–2639, 2004.
+
+\bibitem{Bremler2011} A. Bremler-Barr, Y. Harchol, and D. Hay,
+  ``Space-time tradeoffs in software-based deep packet inspection'',
+  {\it In High Performance Switching and Routing (HPSR), IEEE 12th
+    International Conference on}, pp.1–8, 2011.
+
+\bibitem{Ramakrishnan2010} Ramakrishnan Kandhan, Nikhil Teletia, and
+  Jignesh M. Patel, ``Sigmatch: Fast and scalable multi-pattern
+  matching'', {\it Proceedings of the VLDB Endowment}, 3(1),
+  pp.1173–1184, 2010.
+
+\bibitem{Zhou2007} Zongwei Zhou, Yibo Xue, Junda Liu, Wei Zhang, and
+  Jun Li, ``MDH: A high speed multi-phase dynamic hash string matching
+  algorithm for large-scale pattern set'', {\it Information and
+    Communications Security Springer}, pp.201-215, 2007.
+
+\bibitem{Zhan2014} P. Zhan, W. Yuping, and X. Jinfeng, ``An improved
+  multi-pattern matching algorithm for large-scale pattern sets'',
+  {\it In Computational Intelligence and Security (CIS), Tenth
+    International Conference on}, pp.197–200, 2014.
+
+\bibitem{Zhang2009} Baojun Zhang, Xiaoping Chen, Xuezeng Pan, and
+  Zhaohui Wu, ``High concurrence wu-manber multiple patterns matching
+  algorithm'', {\it Proceedings of the International Symposium on
+    Information Proces}, pp.404-409, 2009.
+
+\bibitem{Choi2011} Yoon-Ho Choi, Moon-Young Jung, and Seung-Woo Seo,
+  ``A fast pattern matching algorithm with multi-byte search unit for
+  highspeed network security'', {\it Computer Communications}, 34(14),
+  pp.1750–1763, 2011.
+
+\bibitem{Le2013} Hoang Le and V.K. Prasanna, ``A memory-efficient and
+  modular approach for large-scale string pattern matching'', {\it
+    Computers, IEEE Transactions on}, 62 (5), pp.844–857, 2013.
+
+\bibitem{Moraru2013} Iulian Moraru and David G. Andersen, ``Exact
+  pattern matching with feed-forward bloom filters'', {\it Journal of
+    Experimental Algorithmics}, Vol.17, pp.3-4, 2013.
+
+\bibitem{Karp1987} R. M. Karp and M. O. Rabin, ``Efficient randomized
+  patternmatching algorithms'', {\it IBM Journal of Research and
+    Development}, 31 (2), pp.249-260, 1987.
+
+\bibitem{Agarwal2013} K. Agarwal and R. Polig, ``A high-speed and
+  large-scale dictionary matching engine for information extraction
+  systems'',{\it Application-Specific Systems, Architectures and
+    Processors (ASAP), IEEE 24th International Conference on},
+  pp.59–66, 2013.
+
+\bibitem{Zhang2015} Hongli Zhang, Dongliang Xu, Zhihong Tian, and
+  Yujian Fan, ``An efficient parallel algorithm for exact
+  multi-pattern matching'', {\it Security And Communication Networks},
+  8 (9), pp.1688–1697, 2015.
+
+\bibitem{I2015} Tomohiro I, Takaaki Nishimoto, Shunsuke Inenaga, Hideo
+  Bannai, and Masayuki Takeda, ``Compressed automata for dictionary
+  matching'', {\it Theoretical Computer Science}, Vol.578, pp.30–41,
+  2015.
+
+\bibitem{Khancome2013} Chouvalit Khancome and Veera Boonjing, ``A new
+  linear-time dynamic dictionary matching algorithm'', {\it Computing
+    And Informatics}, 32 (5), pp.897–923, 2013.
+
+\bibitem{Amir2015} Amihood Amir, Avivit Levy, Ely Porat, and B. Riva
+  Shalom, ``Dictionary matching with a few gaps'', {\it Theoretical
+    Computer Science}, Vol.589, pp.34–46, 2015.
+
+\bibitem{Neuburger2012} Shoshana Neuburger and Dina Sokol. ``Succinct
+  2d dictionary matching'', {\it Algorithmica}, 65 (3), pp.662–684,
+  2012.
+
+\bibitem{Leis2013} V. Leis, A. Kemper, and T. Neumann. ``The adaptive
+  radix tree: Artful indexing for main-memory databases'', {\it In
+    Data Engineering(ICDE), IEEE 29th International Conference on},
+  pp.38–49, 2013.
+
+\bibitem{Ramakrishna1997} M. V. Ramakrishna and Justin
+  Zobel. ``Performance in practice of string hashing functions'', {\it
+    In Proceedings of the Fifth International Conference on Database
+    Systems for Advanced Applications (DASFAA)}, pp.215–224, 1997.
+
+\bibitem{Kim2015} Kim, HyunJin AND Choi, Kang-Il AND Choi,
+  Sang-Il. ``A Memory-Efficient Deterministic Finite Automaton-Based
+  Bit-Split String Matching Scheme Using Pattern Uniqueness in Deep
+  Packet Inspection'', {\it PLOS ONE}. vol.10, pp.1-24, 2015.
+
+\bibitem{pizzachil} {\it http://pizzachil.dcc.uchile.cl/}
+
+\end{thebibliography}
+
+\vspace*{-0.01in}
+%\vspace*{-0.3in}
+\noindent
+\rule{12.6cm}{.1mm}
 
 \end{document}
-
-% which means the suffix set is actually the
-% original whole pattern set)
-
-% \begin{tikzpicture}[scale=1.8]
-
-% %\filldraw[fill=red, draw=green] (0,0) circle [ radius=1cm];
-% \shade[left color=red, right color=black] (0,0) rectangle (1,1);
-% \shadedraw[ball color=yellow, draw=balck] (1.5,0.5) circle [radius=0.5];
-% \draw (-1.5,0)--(1.5,0);
-% \draw (0,-1.5)--(0,1.5);
-% \draw[rotate=45] (0,0) rectangle (0.5,0.5);
-% \draw (0,0) rectangle (1,1);
-% \fill[green!20!white] (0,0) -- (1cm,0) -- arc[start angle=0, end angle=30, radius=1cm]--(0cm,0cm);
-% \draw (-1,-1) rectangle (-0.5,-0.5);
-% \draw (3mm,0mm) arc [start angle=45, end angle=110, radiu
-% s=3mm];$PF$$PF$$PF$
-% \end{tikzpicture}
 
